---
title: "00_data_preparation"
format: md
editor: visual
---

## Data preparation

```{r, include=F, echo=T, warning=F, message=F}
library(tidyverse)
library(tidytext)

library(poetRee)
```

### PoeTree data

Select authors from PoeTree (based on Kjetsaa's list of authors + Fet A.A.)

```{r, include=T, echo=T}
poetree_authors <- get_authors(corpus = "ru") %>% 
  filter(str_detect(name, "Pushkin A.S.|Baratynsk|Lermontov|Zhukovsk|Vjazemsk|Tjutch|Ryleev|Batju|Koltsov|Delvig|Bestuzhev|Kjuhelb|Glinka F.N.|Jazykov|Benediktov|Kozlov I.I.|Shevyr|Polezh|Homja|Venevit|Fet")) %>% 
  select(id_, name)

poetree_authors
```

Get texts ids using authors' ids

```{r, echo=T, results='hide'}
poem_ids <- get_poems(corpus = "ru", authors = poetree_authors$id_)

glimpse(poem_ids)
```

Get texts

```{r, eval = F, echo=T}
vec_ids <- poem_ids$id_[1:3]

head(vec_ids) 
length(vec_ids) # 4842 poems

# call each text separately with lapply + catch errors where the function stopped
texts_list <- lapply(vec_ids, function(id){
  tryCatch( # try except
    get_text(corpus = "ru", poem_id = id),
    error = function(e) tibble(error = e$message, poem_id = id) 
    # if error attach info to relevant columns
  )
})

texts <- bind_rows(texts_list)

glimpse(texts)
```

Check errors

```{r, eval=F, echo=T}
errors <- texts %>% 
  filter(!is.na(error)) %>% 
  pull(poem_id)

poem_ids %>% 
  filter(id_ %in% errors)
```

```{r, eval=F, include=F, echo=F}
# Remove errors from data

ru_poetree <- texts %>% 
  # filter(is.na(error)) %>% # remove errors & error columns
  # select(-error, -poem_id) %>% 
  # add text and author data
  left_join(poem_ids %>% rename(id_poem = id_), by = "id_poem") %>% 
  left_join(poetree_authors %>% rename(id_author = id_), by = "id_author") %>% 
  
  # group lines back to texts
  group_by(id_poem) %>% 
  mutate(poem_text = paste0(line_text, collapse = " \n ")) %>% 
  ungroup() %>% 
  # remove columns
  select(-c(line_text, id_line, id_stanza, id_source, duplicate)) %>% 
  distinct() %>% 
  rename(author_name = name)

# filter texts written before 1810 or after 1839
# ru_poetree <- ru_poetree %>% 
#   filter(!year_created_from < 1810 & !year_created_from > 1839) %>% 
#   filter(!year_created_to < 1810 & !year_created_to > 1839)

glimpse(ru_poetree)
```

Tokenization

```{r, eval=F, echo=T}
ru_poetree_tokens <- ru_poetree %>% 
  unnest_tokens(input = poem_text, output = word, token = "words")
```

Write data

```{r, eval = FALSE, echo=T}
#write.csv(ru_poetree, file = "../data/large_poetree_ru_19c.csv") # full texts
write.csv(ru_poetree_tokens, file = "../data/large_poetree_ru_19c_tokens.csv") # tokenized
```

NB: Next step: lemmatize the tokenized file with `00_lemmatization.ipynb` notebook!

### Kjetsaa's corpus

Load manually prepared data

```{r, echo=T, include=T}
kjetsaa <- read.delim("../data/kjetsaa_norm_corpus.csv", sep = ";") %>% 
  select(-X, -text_raw, -note)

ru_poetree <- read_csv("../data/large_poetree_ru_19c_lemma.csv") %>% select(-`...1`)

glimpse(kjetsaa)
```

Add author names transliteration

```{r, eval=F, echo=T}
# load prepared poetree data if needed
# ru_poetree <- read.csv("../data/poetree_ru_1810-1839.csv")

authors_translit <- tibble(
  author_name = unique(ru_poetree$author_name),
  author_name_ru = c("Е. А. Баратынский", "К. Н. Батюшков", "В. Г. Бенедиктов", 
                     "А. А. Бестужев-Марлинский", "А. А. Дельвиг", 
                     " А. А. Фет",
                     "Ф. Н. Глинка", "А. С. Хомяков", "Н. М. Языков", 
                     "В. К. Кюхельбекер",  "А. В. Кольцов", "И. И. Козлов", 
                     "М. Ю. Лермонтов", "А. И. Полежаев", "А. С. Пушкин", 
                     "К. Ф. Рылеев", "С. П. Шевырев", "Ф. И. Тютчев", 
                     "Д. В. Веневитинов",
                     "П. А. Вяземский", "В. А. Жуковский"
                     )
)

authors_translit
```

Attach transliterated names and tokenize

```{r, eval=F, echo=T}
kjetsaa_tokens <- kjetsaa %>% 
  rename(author_name_ru = author) %>% 
  left_join(authors_translit, by = "author_name_ru") %>% 
  unnest_tokens(input = text_final, output = word, token = "words")
```

Write tokenized df  –\> to be lemmatized with `00_lemmatization.ipynb`

```{r, eval = F, echo=T}
write.csv(kjetsaa_tokens, file = "../data/kjetsaa_norm_tokens.csv")
```

## Data overview

Load prepared data

### poetree

```{r, include=T, echo=T}
poetree_ru <- read.csv("../data/large_poetree_ru_19c_lemma.csv") %>% select(-X)

glimpse(poetree_ru)
```

Number of unique words:

```{r, include=T, echo=T}
poetree_ru %>% 
  count(lemma) %>% nrow()
```

Proportion of words written by each author

```{r, include=T, echo=T}
poetree_ru %>% 
  select(author_name, lemma) %>% 
  group_by(author_name) %>% 
  count(sort = T, name = "n_words") %>% 
  ungroup() %>% 
  mutate(perc = round(n_words / nrow(poetree_ru) * 100, 1))
```

### Kjetsaa's norm corpus

```{r, include=T, echo=T}
kjetsaa_norm <- read.delim("../data/kjetsaa_norm_corpus.csv", sep = ";") %>% 
  select(-X)

# number of lines
kjetsaa_norm %>% 
  separate_rows(text_final, sep = "\n") %>% 
  filter(text_final != "") %>% 
  nrow()

nrow(kjetsaa_norm) # number of texts
```

Number of words & lemmas

```{r, echo=T, include=T}
kjetsaa_lemma <- read_csv("../data/kjetsaa_norm_lemma.csv")

# number of words
nrow(kjetsaa_lemma) 

# number of lemmas
kjetsaa_lemma %>% 
  count(lemma) %>% nrow()
```
