---
title: "01_TTR"
format: html
editor: visual
---

## TTR

## Load data & pckg

This notebook replicates Kjetsaa's plot on TTR in poetic corpora.

```{r}
library(tidyverse)
library(tidytext)

library(MetBrewer)
library(ggbump)
library(cowplot)

theme_set(theme_minimal())
```

Load data

```{r}
# corpus with all words from RNC by 20 authors
corpus <- read.csv("../data/poetree_ru_19c_lemma.csv") %>% 
  # some fixes with colum names etc.
  select(-X) %>% 
  rename(author = author_name)

glimpse(corpus)
```

## Analysis

### Sampling

Number of tokens per author

```{r}
corpus %>% 
  count(author, sort = T)
```

Create a subset with authors \> 30k tokens

```{r}
# create list of authors with more than 30k tokens
authors_30k <- corpus %>% 
  count(author, sort = T) %>% 
  filter(n > 30000) %>% 
  pull(author)

authors_30k # 10 authors
```

```{r}
# 30000k min corpora => 200 words step samples, 150 samples total

sample_size <- 200
samples_number <- 150

corpus_sampled <- corpus %>% 
  filter(author %in% c("Lermontov M.Ju.", "Tjutchev F.I.", "Baratynskij E.A.")) %>% 
  # filter(author == "М. Ю. Лермонтов") %>% 
  group_by(author) %>% 
  # total sample size
  sample_n(30000) %>% 
  # create samples for each author
  mutate(sample_x = sample(
    rep(
      1:samples_number, each = sample_size # 150 samples with 200 words
    )
  )) %>% 
  # add author's name to sample
  unite(sample_id, c(author, sample_x), remove = F) %>% 
  ungroup()


# quick check
head(corpus_sampled)
corpus_sampled %>% count(sample_id) %>% 
  ungroup() %>% sample_n(10) # 150 samples with 200 words
```

```{r}
# simple TTR example
corpus_sampled %>% 
  filter(author %in% c("Lermontov M.Ju.", "Tjutchev F.I.", "Baratynskij E.A.")) %>% 
  group_by(author) %>% 
  # first we have number of tokens
  sample_n(1000) %>% 
  # then select only unique words
  select(author, lemma) %>% 
  distinct() %>% 
  # count their number
  count() %>% 
  ungroup()
```

### 3 authors replication

Replication of Kjetsaa's 1973 figure

```{r}
v <- c(1:samples_number) # vector to count samples

# tibble to store results
df <- tibble(author = NULL, 
             n = NULL)
s <- NULL
x <- NULL

for (i in 1:length(v)) {
  s <- v[1:i] # iterator that takes 1, then 1 2, then 1 2 3, etc.
  
  x <- corpus_sampled %>% 
      filter(author %in% c("Lermontov M.Ju.", "Tjutchev F.I.", "Baratynskij E.A.")) %>% 
      filter(sample_x %in% c(s)) %>% 
      select(author, lemma) %>% 
      distinct() %>% 
      ungroup() %>% 
      count(author) %>%  
      # add column with total number of tokens (n_samples * sample size)
      mutate(n_tokens = s[i] * sample_size)
  
  df <- rbind(df, x)
}


# find max number of lemma
max <- df %>% 
  group_by(author) %>% 
  slice_max(n) %>% ungroup() %>% 
  rename(max_lemma = n,
         max_n_tokens = n_tokens)

plot_1 <- df %>% 
  # attach max lemma values for annotation
  # left_join(max, by = "author") %>% 
  ggplot(aes(x = n_tokens, y = n,
         group = author, colour = author)) + 
  #geom_point() + 
  geom_line(aes(lty = author), linewidth = 1.2) + 
  labs(y = "N types (lemmas)", x = "N tokens") + 
  scale_linetype_manual(values = c(3,1,2)) + 
  scale_colour_manual(values = c(met.brewer("Java")[1],
                                 met.brewer("Java")[5],
                                 met.brewer("Java")[2])) + 
  scale_x_continuous(breaks = seq(0, 31000, by = 5000), 
                     limits = c(0, 34000)) + 
  scale_y_continuous(breaks = seq(1000, 7000, by = 1000),
                     limits = c(0, 7000)) + 
  geom_point(data = max, 
             aes(x = max_n_tokens, y = max_lemma, group = author),
             show.legend = FALSE) + 
  geom_text(data = max %>% filter(author != "Baratynskij E.A."), 
            aes(x = max_n_tokens, y = max_lemma, label = max_lemma), 
            hjust = -0.2, size = 8,
            show.legend = FALSE) + 
  geom_text(data = max %>% filter(author == "Baratynskij E.A."),
            aes(x = max_n_tokens, y = max_lemma, label = max_lemma), 
            hjust = -0.2, vjust = -0.5, size = 8, show.legend = FALSE) +
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 18),
        legend.text = element_text(size = 16),
        legend.position = "bottom",
        legend.title = element_blank())

plot_1

# ggsave("../plots/01_ttr_3-authors.png", plot = last_plot(),
#        width = 6.5, height = 6, bg = "white", dpi = 300)
```

### largest authorial corpora

Select authors with the biggest corpora & find when the TTR growth stops

```{r}
sample_size <- 200
samples_number <- 600

corpus_sampled <- corpus %>% 
  filter(author %in% c("Zhukovskij V.A.", "Pushkin A.S.", "Lermontov M.Ju.")) %>% 
  # filter(author == "М. Ю. Лермонтов") %>% 
  group_by(author) %>% 
  # total sample size
  sample_n(120000) %>% 
  # create 5 samples for each author
  mutate(sample_x = sample(
    rep(
      1:samples_number, each = sample_size # 600 samples with 200 words
    )
  )) %>% 
  # add author's name to sample
  unite(sample_id, c(author, sample_x), remove = F) 


# quick check
head(corpus_sampled)
corpus_sampled %>% count(sample_id) %>% head()
```

Draw curves & find max

```{r}
v <- c(1:samples_number) # vector to count samples

# tibble to store results
df <- tibble(author = NULL, 
             n = NULL)
s <- NULL
x <- NULL

for (i in 1:length(v)) {
  s <- v[1:i] # iterator that takes 1, then 1 2, then 1 2 3, etc.
  
  x <- corpus_sampled %>% 
      filter(sample_x %in% c(s)) %>% 
      select(author, lemma) %>% 
      distinct() %>% 
      ungroup() %>% 
      count(author) %>%  
      # add column with total number of tokens (n_samples * sample size)
      mutate(n_tokens = s[i] * sample_size)
  
  df <- rbind(df, x)
}


# find max number of lemma
max <- df %>% 
  group_by(author) %>% 
  slice_max(n) %>% ungroup() %>% 
  rename(max_lemma = n,
         max_n_tokens = n_tokens)

plot_2 <- df %>% 
  # attach max lemma values for annotation
  # left_join(max, by = "author") %>% 
  ggplot(aes(x = n_tokens, y = n,
         group = author, colour = author)) + 
  #geom_point() + 
  geom_line(aes(lty = author), linewidth = 1.2) + 
  labs(y = "N types (lemmas)", x = "N tokens") + 
  scale_linetype_manual(values = c(1,3,2)) + 
  scale_colour_manual(values = c(met.brewer("Java")[5],
                                 met.brewer("Java")[3],
                                 met.brewer("Java")[1])) + 
  scale_x_continuous(breaks = seq(10000, 125000, by = 35000), 
                     limits = c(0, 145000)) + 
  #scale_y_continuous(breaks = seq(1000, 6000, by = 1000),
  #                   limits = c(0, 6000)) + 
  geom_point(data = max, 
             aes(x = max_n_tokens, y = max_lemma, group = author),
             show.legend = FALSE) + 
  geom_text(data = max, 
            aes(x = max_n_tokens, y = max_lemma, label = max_lemma), 
            hjust = -0.2, size = 8, 
            show.legend = FALSE) + 
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 18),
        legend.text = element_text(size = 16),
        legend.position = "bottom",
        legend.title = element_blank())

plot_2

# ggsave("../plots/02_ttr_120k.png", plot = last_plot(),
#       width = 6.5, height = 6, bg = "white", dpi = 300)
```

### more samples & authors

```{r}
corpus %>% 
  filter(author %in% authors_30k) %>% 
  group_by(author) %>% 
  count(sort = T)
```

Draw curves for 11 authors with corpus size \>30k

```{r}
# 30000k min corpora => 200 words step samples, 150 samples total

sample_size <- 200
samples_number <- 150

corpus_sampled <- corpus %>% 
  filter(author %in% authors_30k) %>% 
  # filter(author == "М. Ю. Лермонтов") %>% 
  group_by(author) %>% 
  # total sample size
  sample_n(30000) %>% 
  # create samples for each author
  mutate(sample_x = sample(
    rep(
      1:samples_number, each = sample_size # 150 samples with 200 words
    )
  )) %>% 
  # add author's name to sample
  unite(sample_id, c(author, sample_x), remove = F) %>% 
  ungroup()
```

```{r}
v <- c(1:samples_number) # vector to count samples

# tibble to store results
df <- tibble(author = NULL, 
             n = NULL)
s <- NULL
x <- NULL

for (i in 1:length(v)) {
  s <- v[1:i] # iterator that takes 1, then 1 2, then 1 2 3, etc.
  
  x <- corpus_sampled %>% 
      filter(sample_x %in% c(s)) %>% 
      select(author, lemma) %>% 
      distinct() %>% 
      ungroup() %>% 
      count(author) %>%  
      # add column with total number of tokens (n_samples * sample size)
      mutate(n_tokens = s[i] * sample_size)
  
  df <- rbind(df, x)
}


# find max number of lemma
max <- df %>% 
  group_by(author) %>% 
  slice_max(n) %>% ungroup() %>% 
  rename(max_lemma = n,
         max_n_tokens = n_tokens) %>% 
  mutate(author_is = ifelse(author == "Lermontov M.Ju.", 
                            "Lermontov M.Ju.", "Other authors"))

plot_3 <- df %>% 
#  mutate(author_is = ifelse(author == "Lermontov M.Ju.", 
#                            "Lermontov M.Ju.", "Other authors")) %>% 
  
  # attach max lemma values for annotation
  left_join(max, by = "author") %>% 
  ggplot(aes(x = n_tokens, y = n,
         group = author, colour = author_is)) + 
  #geom_point() + 
  geom_line(#aes(lty = author_is), 
            linewidth = 1.2, alpha = 0.6) + 
  labs(y = "N types (lemmas)", x = "N tokens") + 
  #scale_linetype_manual(values = c(1,3,2)) + 
  scale_colour_manual(values = c(met.brewer("Java")[5],
                                 met.brewer("Kandinsky")[3],
                                 met.brewer("Java")[2],
                                 met.brewer("Archambault"),
                                 met.brewer("Cassatt1"))) + 
  scale_x_continuous(breaks = seq(0, 30000, by = 5000), 
                     limits = c(0, 34000)) + 
  #scale_y_continuous(breaks = seq(1000, 6000, by = 1000),
  #                   limits = c(0, 6000)) + 
  geom_point(data = max, 
             aes(x = max_n_tokens, y = max_lemma, group = author),
             show.legend = FALSE) + 
  geom_text(data = max  %>% filter(author %in% c("Lermontov M.Ju.", 
                                               "Vjazemskij P.A.")), 
            aes(x = max_n_tokens, y = max_lemma, label = max_lemma), 
            hjust = -0.2, size = 8, 
            show.legend = FALSE) + 
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 18),
        legend.text = element_text(size = 16),
        legend.position = "bottom",
        legend.title = element_blank())

plot_3

ggsave("../plots/03_ttr_11authors.png", plot = last_plot(),
      width = 7, height = 6, bg = "white", dpi = 300)
```

### fig 1

Merge plots to figure 1

```{r}
library(jpeg)
library(magick)
img <- readJPEG("../plots/Kjetsaa_1973_fig1.jpg")

# draw an empty plot
plot_0 <- df %>% 
  ggplot(aes(x = n_tokens, y = n,
         group = author, colour = author)) + 
  labs(x = "", y = "") + #theme(axis.text = element_blank())
  draw_image(img, width = 1.4, height = 1.4,
             x = -0.25, y = -0.1)


plot_0
```

```{r}
plot_grid(plot_0, plot_1, plot_2, plot_3,
          align = "h", nrow = 2, labels = c('A', 'B', 'C', 'D'), label_size = 36,
          scale = c(1, 0.8, 0.8, 0.8))

ggsave("../plots/fig_1.png", plot = last_plot(), 
       bg = "white", dpi = 300,
       width = 20, height = 16)
```

### % of unique words

Next step: Sample size (x) to % of unique words out of sample: check lermontov

```{r}
# # create list of authors with more than 10k tokens
# authors_10k <- corpus %>% 
#   count(author, sort = T) %>% 
#   filter(n > 10000) %>% 
#   pull(author)

sample_size <- 200
samples_number <- 150

corpus_sampled <- corpus %>% 
  filter(author %in% authors_30k) %>% 
  # filter(author == "М. Ю. Лермонтов") %>% 
  group_by(author) %>% 
  # total sample size
  sample_n(30000) %>% 
  # create 5 samples for each author
  mutate(sample_x = sample(
    rep(
      1:samples_number, each = sample_size # 150 samples with 200 words
    )
  )) %>% 
  # add author's name to sample
  unite(sample_id, c(author, sample_x), remove = F) 

v <- c(1:samples_number) # vector to count samples

# tibble to store results
df <- tibble(author = NULL, 
             n = NULL)
s <- NULL
x <- NULL

for (i in 1:length(v)) {
  s <- v[1:i] # iterator that takes 1, then 1 2, then 1 2 3, etc.
  
  x <- corpus_sampled %>% 
      filter(sample_x %in% c(s)) %>% 
      select(author, lemma) %>% 
      distinct() %>% 
      ungroup() %>% 
      count(author) %>%  
      # add column with total number of tokens (n_samples * sample size)
      mutate(n_tokens = s[i] * sample_size)
  
  df <- rbind(df, x)
}


# find max number of lemma
max <- df %>% 
  group_by(author) %>% 
  slice_max(n) %>% ungroup() %>% 
  rename(max_lemma = n,
         max_n_tokens = n_tokens)




df %>% 
  #filter(author %in% c("А. С. Пушкин", "М. Ю. Лермонтов")) %>% 
  #filter(run == 20) %>% 
  mutate(group = ifelse(author == "Lermontov M.Ju.", "Our poet", "Others")) %>% 
  
  mutate(perc = round((n/n_tokens) *100, 2)) %>% 
  ggplot(aes(x = n_tokens, y = perc, colour = author)) + 
  geom_line(aes(lty = group), linewidth = 1) + 
  labs(y = "% lemmas", x = "N tokens") + 
  # scale_linetype_manual(values = c(2,1,2)) + 
  # scale_colour_manual(values = c(met.brewer("Java")[1],
  #                                met.brewer("Java")[5],
  #                                met.brewer("Java")[2])) + 
  #scale_x_continuous(breaks = seq(6000, 30000, by = 6000), 
  #                   limits = c(0, 36000)) + 
  #scale_y_continuous(breaks = seq(1000, 6000, by = 1000),
  #                   limits = c(0, 6000)) + 
  #geom_point(data = max, 
  #           aes(x = max_n_tokens, y = max_lemma, group = author)) + 
  #geom_text(data = max, 
  #          aes(x = max_n_tokens, y = max_lemma, label = max_lemma), 
  #          hjust = -0.2, size = 8) + 
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 18),
        legend.text = element_text(size = 16), 
        plot.title = element_text(size = 20)) + 
  labs(colour = "", lty = "", 
       title = "% of unique words given sample size")


# ggsave("../plots/04_TTR_perc.png", plot = last_plot(),
#       width = 8, height = 6, bg = "white", dpi = 300)
```

## boxplots

### 30k authors

```{r}

i <- NULL
df <- NULL

# 100 iterations
for (i in 1:100) {
  corpus_smpl <- corpus %>% 
    filter(author %in% authors_30k) %>% 
    group_by(author) %>% 
    # sample random 10k words
    sample_n(30000) %>% 
    count(word) %>% 
    ungroup() %>% 
    count(author)

  df <- rbind(df, corpus_smpl)
}

glimpse(df)

plot_2a <- df %>% 
  mutate(author_is = ifelse(author == "Lermontov M.Ju.", "Lermontov M.Ju.", "Others")) %>% 
  ggplot(aes(x = reorder(author, -n, mean), y = n)) + 
  geom_boxplot(aes(fill = author_is, colour = author_is), alpha = 0.6) + 
  labs(x = "", 
       y = "N types (unique words)",
       fill = "", colour = "",
       subtitle = "30 000 word samples, 100 iterations") + 
  scale_fill_manual(values = c(met.brewer("Java")[5],
                               met.brewer("Java")[4])) + 
  scale_colour_manual(values = c(met.brewer("Java")[5],
                               met.brewer("Java")[4])) + 
  theme(
    axis.text = element_text(size = 16),
    axis.text.x = element_text(angle = 90),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    plot.subtitle = element_text(size = 18),
    legend.position = "None"
  )

plot_2a

# ggsave("../plots/00_ttr_30ksamples.png", plot = last_plot(), 
#        dpi = 300, bg = "white", 
#        width = 9, height = 7)
```

### 2k samples

```{r}
i <- NULL
df_2k <- NULL

# 100 iterations
for (i in 1:100) {
  corpus_smpl <- corpus %>% 
    filter(author %in% authors_30k) %>% 
    group_by(author) %>% 
    # sample random 2k words
    sample_n(2000) %>% 
    count(word) %>% 
    ungroup() %>% 
    count(author)

  df_2k <- rbind(df_2k, corpus_smpl)
}

glimpse(df_2k)

plot_2b <- df_2k %>% 
  mutate(author_is = ifelse(author == "Lermontov M.Ju.", "Lermontov M.Ju.", "Others")) %>% 
  ggplot(aes(x = reorder(author, -n, mean), y = n)) + 
  geom_boxplot(aes(fill = author_is, colour = author_is), alpha = 0.6) + 
  labs(x = "", 
       y = "N types (unique words)",
       fill = "", colour = "",
       subtitle = "2000 words samples, 100 iterations") + 
  scale_fill_manual(values = c(met.brewer("Java")[5],
                               met.brewer("Java")[4])) + 
  scale_colour_manual(values = c(met.brewer("Java")[5],
                               met.brewer("Java")[4])) + 
  theme(
    axis.text = element_text(size = 16),
    axis.text.x = element_text(angle = 90),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    plot.subtitle = element_text(size = 18),
    legend.position = "None"
  )

plot_2b

# ggsave("../plots/00_ttr_2ksamples.png", plot = last_plot(), 
#        dpi = 300, bg = "white", 
#        width = 9, height = 7)
```

### 

TTR in Kjetsaa's norm:

```{r}
norm <- read.csv("../data/kjetsaa_norm_lemma.csv")
glimpse(norm)
```

```{r}
norm %>% 
  count(author_name, sort = T)

glimpse(norm)
```

Add some random words to have 2k samples for all authors

```{r}
sh <- corpus %>% 
  filter(author == "Shevyrev S.P.") %>% 
  sample_n(20) %>% 
  select(author, word, lemma)

bar <- corpus %>% 
  filter(author == "Baratynskij E.A.") %>% 
  sample_n(55) %>% 
  select(author, word, lemma)

tjut <- corpus %>% 
  filter(author == "Tjutchev F.I.") %>% 
  sample_n(147) %>% 
  select(author, word, lemma)

bat <- corpus %>% 
  filter(author == "Batjushkov K.N.") %>% 
  sample_n(164) %>% 
  select(author, word, lemma)

```

```{r}
# sample words for authors with >2k 
norm_2k <- norm %>% 
  filter(!author_name %in% c("Shevyrev S.P.", "Baratynskij E.A.",
                        "Tjutchev F.I.", "Batjushkov K.N.")) %>% 
  group_by(author_name) %>% 
  sample_n(2000) %>% 
  select(author_name, word, lemma) %>% 
  ungroup()

# select 4 authors with <2k
norm_4a <- norm %>% 
  filter(author_name %in% c("Shevyrev S.P.", "Baratynskij E.A.",
                        "Tjutchev F.I.", "Batjushkov K.N.")) %>% 
  select(author_name, word, lemma)

# attach random samples
norm_4a <- norm_4a %>% 
  rename(author = author_name) %>% 
  rbind(bar, bat, tjut, sh) 

# check n words
norm_2k %>% 
  rename(author = author_name) %>% 
  rbind(norm_4a) %>% 
  count(author)

norm_2k_all <- norm_2k %>% 
  rename(author = author_name) %>% 
  rbind(norm_4a) 
```

Count N lemmas

```{r}
norm_types <- norm_2k_all %>% 
  group_by(author) %>% 
  count(word) %>% 
  ungroup() %>% 
  count(author) %>% 
  rename(n_kjetsaa = n)

norm_types
```

### fig 2

```{r}
plot_2b <- df_2k %>% 
  left_join(norm_types, by = "author") %>% 
  filter(author != "Fet A.A.") %>% 
  
  mutate(author_is = ifelse(author == "Lermontov M.Ju.", "Lermontov M.Ju.", "Others")) %>% 
  ggplot(aes(x = reorder(author, -n, mean), y = n)) + 
  geom_boxplot(aes(fill = author_is, colour = author_is), alpha = 0.6) + 
  
  geom_point(aes(x = author, y = n_kjetsaa), 
             shape = 17, colour = met.brewer("Java")[1], 
             size = 5, alpha = 0.7) + 
  
  labs(x = "", 
       y = "N types (unique words)",
       fill = "", colour = "",
       subtitle = "2000 words samples, 100 iterations",
       caption = "* Violet triangles are the 2000 word samples\nfrom the replicated Kjetsaa's Norm corpus") + 
  scale_fill_manual(values = c(met.brewer("Java")[5],
                               met.brewer("Java")[4])) + 
  scale_colour_manual(values = c(met.brewer("Java")[5],
                               met.brewer("Java")[4])) + 
  scale_y_continuous(limits = c(1090, 1420),
    breaks = seq(1100, 1400, 100)) + 
  theme(
    axis.text = element_text(size = 16),
    axis.text.x = element_text(angle = 90),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    plot.subtitle = element_text(size = 18),
    legend.position = "None",
    plot.caption = element_text(hjust = 0, size = 14)
  ) 



plot_2b
```

```{r}
plot_grid(plot_2a, plot_2b, align = "h", nrow = 1, 
          labels = c('A', 'B'), scale = 0.9, label_size = 24)

ggsave("../plots/fig_2.png", plot = last_plot(), 
       dpi = 300, bg = "white", 
       width = 12, height = 7)
```
