---
title: "01_TTR"
format: html
editor: visual
---

## TTR

## Load data & pckg

This notebook replicates Kjetsaa's plot on TTR in poetic corpora.

```{r}
library(tidyverse)

library(MetBrewer)
library(ggbump)
library(cowplot)

theme_set(theme_minimal())
```

Load data

```{r}
# corpus with all words from RNC by 20 authors
corpus <- read.csv("../data/poetree_ru_19c_lemma.csv") %>% 
  # some fixes with colum names etc.
  select(-X) %>% 
  rename(author = author_name)

glimpse(corpus)
```

## Analysis

### Sampling

Number of tokens per author

```{r}
corpus %>% 
  count(author, sort = T)
```

Create a subset with authors \> 30k tokens

```{r}
# create list of authors with more than 30k tokens
authors_30k <- corpus %>% 
  count(author, sort = T) %>% 
  filter(n > 30000) %>% 
  pull(author)

authors_30k # 10 authors
```

```{r}
# 30000k min corpora => 200 words step samples, 150 samples total

sample_size <- 200
samples_number <- 150

corpus_sampled <- corpus %>% 
  filter(author %in% c("Lermontov M.Ju.", "Tjutchev F.I.", "Baratynskij E.A.")) %>% 
  # filter(author == "М. Ю. Лермонтов") %>% 
  group_by(author) %>% 
  # total sample size
  sample_n(30000) %>% 
  # create samples for each author
  mutate(sample_x = sample(
    rep(
      1:samples_number, each = sample_size # 150 samples with 200 words
    )
  )) %>% 
  # add author's name to sample
  unite(sample_id, c(author, sample_x), remove = F) %>% 
  ungroup()


# quick check
head(corpus_sampled)
corpus_sampled %>% count(sample_id) %>% 
  ungroup() %>% sample_n(10) # 150 samples with 200 words
```

```{r}
# simple TTR example
corpus_sampled %>% 
  filter(author %in% c("Lermontov M.Ju.", "Tjutchev F.I.", "Baratynskij E.A.")) %>% 
  group_by(author) %>% 
  # first we have number of tokens
  sample_n(1000) %>% 
  # then select only unique words
  select(author, lemma) %>% 
  distinct() %>% 
  # count their number
  count() %>% 
  ungroup()
```

### 3 authors replication

Replication of Kjetsaa's 1973 figure

```{r}
v <- c(1:samples_number) # vector to count samples

# tibble to store results
df <- tibble(author = NULL, 
             n = NULL)
s <- NULL
x <- NULL

for (i in 1:length(v)) {
  s <- v[1:i] # iterator that takes 1, then 1 2, then 1 2 3, etc.
  
  x <- corpus_sampled %>% 
      filter(author %in% c("Lermontov M.Ju.", "Tjutchev F.I.", "Baratynskij E.A.")) %>% 
      filter(sample_x %in% c(s)) %>% 
      select(author, lemma) %>% 
      distinct() %>% 
      ungroup() %>% 
      count(author) %>%  
      # add column with total number of tokens (n_samples * sample size)
      mutate(n_tokens = s[i] * sample_size)
  
  df <- rbind(df, x)
}


# find max number of lemma
max <- df %>% 
  group_by(author) %>% 
  slice_max(n) %>% ungroup() %>% 
  rename(max_lemma = n,
         max_n_tokens = n_tokens)

plot_1 <- df %>% 
  # attach max lemma values for annotation
  # left_join(max, by = "author") %>% 
  ggplot(aes(x = n_tokens, y = n,
         group = author, colour = author)) + 
  #geom_point() + 
  geom_line(aes(lty = author), linewidth = 1.2) + 
  labs(y = "N types (lemmas)", x = "N tokens") + 
  scale_linetype_manual(values = c(3,1,2)) + 
  scale_colour_manual(values = c(met.brewer("Java")[1],
                                 met.brewer("Java")[5],
                                 met.brewer("Java")[2])) + 
  scale_x_continuous(breaks = seq(0, 31000, by = 5000), 
                     limits = c(0, 34000)) + 
  scale_y_continuous(breaks = seq(1000, 7000, by = 1000),
                     limits = c(0, 7000)) + 
  geom_point(data = max, 
             aes(x = max_n_tokens, y = max_lemma, group = author),
             show.legend = FALSE) + 
  geom_text(data = max %>% filter(author != "Baratynskij E.A."), 
            aes(x = max_n_tokens, y = max_lemma, label = max_lemma), 
            hjust = -0.2, size = 8,
            show.legend = FALSE) + 
  geom_text(data = max %>% filter(author == "Baratynskij E.A."),
            aes(x = max_n_tokens, y = max_lemma, label = max_lemma), 
            hjust = -0.2, vjust = -0.5, size = 8, show.legend = FALSE) +
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 18),
        legend.text = element_text(size = 16),
        legend.position = "bottom",
        legend.title = element_blank())

plot_1

ggsave("../plots/01_ttr_3-authors.png", plot = last_plot(),
       width = 6.5, height = 6, bg = "white", dpi = 300)
```

### largest authorial corpora

Select authors with the biggest corpora & find when the TTR growth stops

```{r}
sample_size <- 200
samples_number <- 600

corpus_sampled <- corpus %>% 
  filter(author %in% c("Zhukovskij V.A.", "Pushkin A.S.", "Lermontov M.Ju.")) %>% 
  # filter(author == "М. Ю. Лермонтов") %>% 
  group_by(author) %>% 
  # total sample size
  sample_n(120000) %>% 
  # create 5 samples for each author
  mutate(sample_x = sample(
    rep(
      1:samples_number, each = sample_size # 150 samples with 200 words
    )
  )) %>% 
  # add author's name to sample
  unite(sample_id, c(author, sample_x), remove = F) 


# quick check
head(corpus_sampled)
corpus_sampled %>% count(sample_id) %>% head()
```

Draw curves & find max

```{r}
v <- c(1:samples_number) # vector to count samples

# tibble to store results
df <- tibble(author = NULL, 
             n = NULL)
s <- NULL
x <- NULL

for (i in 1:length(v)) {
  s <- v[1:i] # iterator that takes 1, then 1 2, then 1 2 3, etc.
  
  x <- corpus_sampled %>% 
      filter(sample_x %in% c(s)) %>% 
      select(author, lemma) %>% 
      distinct() %>% 
      ungroup() %>% 
      count(author) %>%  
      # add column with total number of tokens (n_samples * sample size)
      mutate(n_tokens = s[i] * sample_size)
  
  df <- rbind(df, x)
}


# find max number of lemma
max <- df %>% 
  group_by(author) %>% 
  slice_max(n) %>% ungroup() %>% 
  rename(max_lemma = n,
         max_n_tokens = n_tokens)

plot_2 <- df %>% 
  # attach max lemma values for annotation
  # left_join(max, by = "author") %>% 
  ggplot(aes(x = n_tokens, y = n,
         group = author, colour = author)) + 
  #geom_point() + 
  geom_line(aes(lty = author), linewidth = 1.2) + 
  labs(y = "N types (lemmas)", x = "N tokens") + 
  scale_linetype_manual(values = c(1,3,2)) + 
  scale_colour_manual(values = c(met.brewer("Java")[5],
                                 met.brewer("Java")[3],
                                 met.brewer("Java")[6])) + 
  scale_x_continuous(breaks = seq(10000, 125000, by = 35000), 
                     limits = c(0, 145000)) + 
  #scale_y_continuous(breaks = seq(1000, 6000, by = 1000),
  #                   limits = c(0, 6000)) + 
  geom_point(data = max, 
             aes(x = max_n_tokens, y = max_lemma, group = author),
             show.legend = FALSE) + 
  geom_text(data = max, 
            aes(x = max_n_tokens, y = max_lemma, label = max_lemma), 
            hjust = -0.2, size = 8, 
            show.legend = FALSE) + 
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 18),
        legend.text = element_text(size = 16),
        legend.position = "bottom",
        legend.title = element_blank())

plot_2

ggsave("../plots/02_ttr_120k.png", plot = last_plot(),
      width = 6.5, height = 6, bg = "white", dpi = 300)
```

### more samples & authors

```{r}
corpus %>% 
  filter(author %in% authors_30k) %>% 
  group_by(author) %>% 
  count(sort = T)
```

Draw curves for 11 authors with corpus size \>30k

```{r}
# 30000k min corpora => 200 words step samples, 150 samples total

sample_size <- 200
samples_number <- 150

corpus_sampled <- corpus %>% 
  filter(author %in% authors_30k) %>% 
  # filter(author == "М. Ю. Лермонтов") %>% 
  group_by(author) %>% 
  # total sample size
  sample_n(30000) %>% 
  # create samples for each author
  mutate(sample_x = sample(
    rep(
      1:samples_number, each = sample_size # 150 samples with 200 words
    )
  )) %>% 
  # add author's name to sample
  unite(sample_id, c(author, sample_x), remove = F) %>% 
  ungroup()
```

```{r}
v <- c(1:samples_number) # vector to count samples

# tibble to store results
df <- tibble(author = NULL, 
             n = NULL)
s <- NULL
x <- NULL

for (i in 1:length(v)) {
  s <- v[1:i] # iterator that takes 1, then 1 2, then 1 2 3, etc.
  
  x <- corpus_sampled %>% 
      filter(sample_x %in% c(s)) %>% 
      select(author, lemma) %>% 
      distinct() %>% 
      ungroup() %>% 
      count(author) %>%  
      # add column with total number of tokens (n_samples * sample size)
      mutate(n_tokens = s[i] * sample_size)
  
  df <- rbind(df, x)
}


# find max number of lemma
max <- df %>% 
  group_by(author) %>% 
  slice_max(n) %>% ungroup() %>% 
  rename(max_lemma = n,
         max_n_tokens = n_tokens) %>% 
  mutate(author_is = ifelse(author == "Lermontov M.Ju.", 
                            "Lermontov M.Ju.", "Other authors"))

plot_3 <- df %>% 
#  mutate(author_is = ifelse(author == "Lermontov M.Ju.", 
#                            "Lermontov M.Ju.", "Other authors")) %>% 
  
  # attach max lemma values for annotation
  left_join(max, by = "author") %>% 
  ggplot(aes(x = n_tokens, y = n,
         group = author, colour = author_is)) + 
  #geom_point() + 
  geom_line(#aes(lty = author_is), 
            linewidth = 1.2, alpha = 0.6) + 
  labs(y = "N types (lemmas)", x = "N tokens") + 
  #scale_linetype_manual(values = c(1,3,2)) + 
  scale_colour_manual(values = c(met.brewer("Java")[5],
                                 met.brewer("Java")[6],
                                 met.brewer("Java")[2],
                                 met.brewer("Archambault"),
                                 met.brewer("Cassatt1"))) + 
  scale_x_continuous(breaks = seq(0, 30000, by = 5000), 
                     limits = c(0, 34000)) + 
  #scale_y_continuous(breaks = seq(1000, 6000, by = 1000),
  #                   limits = c(0, 6000)) + 
  geom_point(data = max, 
             aes(x = max_n_tokens, y = max_lemma, group = author),
             show.legend = FALSE) + 
  geom_text(data = max  %>% filter(author %in% c("Lermontov M.Ju.", 
                                               "Vjazemskij P.A.")), 
            aes(x = max_n_tokens, y = max_lemma, label = max_lemma), 
            hjust = -0.2, size = 8, 
            show.legend = FALSE) + 
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 18),
        legend.text = element_text(size = 16),
        legend.position = "bottom",
        legend.title = element_blank())

plot_3

ggsave("../plots/03_ttr_11authors.png", plot = last_plot(),
      width = 7, height = 6, bg = "white", dpi = 300)
```

### fig 1

Merge plots to figure 1

```{r}
library(jpeg)
library(magick)
img <- readJPEG("../plots/Kjetsaa_1973_fig1.jpg")

# draw an empty plot
plot_0 <- df %>% 
  ggplot(aes(x = n_tokens, y = n,
         group = author, colour = author)) + 
  labs(x = "", y = "") + #theme(axis.text = element_blank())
  draw_image(img, width = 1.4, height = 1.4,
             x = -0.25, y = -0.1)


plot_0
```

```{r}
plot_grid(plot_0, plot_1, plot_2, plot_3,
          align = "h", nrow = 2, labels = c('A', 'B', 'C', 'D'), label_size = 36,
          scale = c(1, 0.8, 0.8, 0.8))

ggsave("../plots/fig_1.png", plot = last_plot(), 
       bg = "white", dpi = 300,
       width = 20, height = 16)
```

## boxplots

```{r}
# sample 10k sample, 200 w step, 50 samples

sample_size <- 200
samples_number <- 50

# tibble to store results
df <- tibble(author = NULL, 
               n = NULL)

for (j in 1:100) { 
  corpus_sampled <- corpus %>% 
    filter(author %in% authors_30k) %>% 
    # filter(author == "М. Ю. Лермонтов") %>% 
    group_by(author) %>% 
    # total sample size
    sample_n(30000) %>% 
    # create 5 samples for each author
    mutate(sample_x = sample(
      rep(
        1:samples_number, each = sample_size # 150 samples with 200 words
      )
    )) %>% 
    # add author's name to sample
    unite(sample_id, c(author, sample_x), remove = F) 
  
  # quick check
  # head(corpus_sampled)
  # corpus_sampled %>% count(sample_id) %>% head()
  
  v <- c(1:samples_number) # vector to count samples
  
  s <- NULL
  x <- NULL
  
  for (i in 1:length(v)) {
    s <- v[1:i] # iterator that takes 1, then 1 2, then 1 2 3, etc.
    
    x <- corpus_sampled %>% 
        filter(sample_x %in% c(s)) %>% 
        select(author, lemma) %>% 
        distinct() %>% 
        ungroup() %>% 
        count(author) %>%  
        # add column with total number of tokens (n_samples * sample size)
        mutate(n_tokens = s[i] * sample_size, 
               run = j) 
    
    df <- rbind(df, x)
  }
}  

glimpse(df)
```

Draw curves

```{r}
# find max number of lemma
max <- df %>% 
  group_by(author, run) %>% 
  slice_max(n) %>% ungroup() %>% 
  rename(max_lemma = n,
         max_n_tokens = n_tokens)

max %>% 
  filter(max_n_tokens != 10000)
```

```{r}
# count ranks withtin each run
max %>% 
  arrange(author, max_lemma) %>% # arrange results for each author
  group_by(run) %>% 
  mutate(rank = rank(-max_lemma)) %>% # create ranks within runs
  ungroup() %>% 
  filter(run == 1) %>% # check
  arrange(rank)

runs_ranks <- max %>% 
  arrange(author, max_lemma) %>% # arrange results for each author
  group_by(run) %>% 
  mutate(rank = rank(-max_lemma)) %>% # create ranks within runs
  ungroup() 

head(runs_ranks)

max %>% filter(author == "Lermontov M.Ju.") %>% 
  pull(max_lemma) %>% 
  mean()
```

```{r}
runs_ranks %>% 
  mutate(group = ifelse(author == "Lermontov M.Ju.", "Our poet", "Others")) %>% 
  ggplot(aes(y = max_lemma, x = reorder(author, max_lemma, mean), 
             group = author, fill = group)) + 
  geom_boxplot() + 
  scale_x_discrete(limits = rev) + 
  scale_fill_manual(values = c(met.brewer("Klimt")[1], 
                                  met.brewer("Java")[5])) + 
  geom_hline(yintercept = 2800, 
             lty = 5, linewidth = 1, 
             colour = met.brewer("Java")[5],
             alpha = 0.7) + 
  labs(x = "Authors", y = "Number of unique words", 
       fill = "", 
       title = "Number of unique words",
       subtitle = "15 authors (>30k tokens)\n10k word samples (random), 100 iterations") + 
  theme(axis.text.x = element_text(angle = 90, size = 12),
        axis.text.y = element_text(size = 16), 
        axis.title = element_text(size = 18), 
        #legend.text = element_blank(),
        legend.position = "None",
        plot.title = element_text(size = 20),
        plot.subtitle = element_text(size = 20))

ggsave("../plots/03_TTR_sample_test.png", plot = last_plot(),
       width = 8, height = 6, bg = "white", dpi = 300)
```

### % of unique words

Next step: Sample size (x) to % of unique words out of sample: check lermontov

```{r}
# create list of authors with more than 10k tokens
authors_10k <- corpus %>% 
  count(author, sort = T) %>% 
  filter(n > 10000) %>% 
  pull(author)

sample_size <- 200
samples_number <- 50

corpus_sampled <- corpus %>% 
  filter(author %in% authors_10k) %>% 
  # filter(author == "М. Ю. Лермонтов") %>% 
  group_by(author) %>% 
  # total sample size
  sample_n(10000) %>% 
  # create 5 samples for each author
  mutate(sample_x = sample(
    rep(
      1:samples_number, each = sample_size # 150 samples with 200 words
    )
  )) %>% 
  # add author's name to sample
  unite(sample_id, c(author, sample_x), remove = F) 

v <- c(1:samples_number) # vector to count samples

# tibble to store results
df <- tibble(author = NULL, 
             n = NULL)
s <- NULL
x <- NULL

for (i in 1:length(v)) {
  s <- v[1:i] # iterator that takes 1, then 1 2, then 1 2 3, etc.
  
  x <- corpus_sampled %>% 
      filter(sample_x %in% c(s)) %>% 
      select(author, lemma) %>% 
      distinct() %>% 
      ungroup() %>% 
      count(author) %>%  
      # add column with total number of tokens (n_samples * sample size)
      mutate(n_tokens = s[i] * sample_size)
  
  df <- rbind(df, x)
}


# find max number of lemma
max <- df %>% 
  group_by(author) %>% 
  slice_max(n) %>% ungroup() %>% 
  rename(max_lemma = n,
         max_n_tokens = n_tokens)




df %>% 
  #filter(author %in% c("А. С. Пушкин", "М. Ю. Лермонтов")) %>% 
  #filter(run == 20) %>% 
  mutate(group = ifelse(author == "Lermontov M.Ju.", "Our poet", "Others")) %>% 
  
  mutate(perc = round((n/n_tokens) *100, 2)) %>% 
  ggplot(aes(x = n_tokens, y = perc, colour = author)) + 
  geom_line(aes(lty = group), linewidth = 1) + 
  labs(y = "% lemmas", x = "N tokens") + 
  # scale_linetype_manual(values = c(2,1,2)) + 
  # scale_colour_manual(values = c(met.brewer("Java")[1],
  #                                met.brewer("Java")[5],
  #                                met.brewer("Java")[2])) + 
  #scale_x_continuous(breaks = seq(6000, 30000, by = 6000), 
  #                   limits = c(0, 36000)) + 
  #scale_y_continuous(breaks = seq(1000, 6000, by = 1000),
  #                   limits = c(0, 6000)) + 
  #geom_point(data = max, 
  #           aes(x = max_n_tokens, y = max_lemma, group = author)) + 
  #geom_text(data = max, 
  #          aes(x = max_n_tokens, y = max_lemma, label = max_lemma), 
  #          hjust = -0.2, size = 8) + 
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 18),
        legend.text = element_text(size = 16), 
        plot.title = element_text(size = 20)) + 
  labs(colour = "", lty = "", 
       title = "% of unique words given sample size")


# ggsave("../plots/04_TTR_perc.png", plot = last_plot(),
#       width = 8, height = 6, bg = "white", dpi = 300)
```

Thoughts on this: seems like it depends on sample size/selection? I.e. for small-sample poets similar poems are selected.

```{r}
runs_ranks %>% 
  mutate(clr = ifelse(author == "Lermontov M.Ju.", "Our author", "Others")) %>% 
  ggplot(aes(x = run, y = max_lemma, group = author, colour = clr)) +
    geom_bump(size = 1, alpha = 0.6) +
    geom_point(size = 2, alpha = 0.6) + 
    scale_color_manual(values = c(met.brewer("Klimt")[1], 
                                  met.brewer("Java")[5])) + 
  labs(x = "Run", y = "Max number of lemmas", 
       colour = "", 
       title = "Number of unique words in 10,000 word samples",
       subtitle = "100 runs") + 
  scale_x_continuous(breaks = seq(1, 100, by = 1)) + 
  scale_y_continuous(breaks = seq(3000, 6000, by = 250)) + 
  theme(axis.text = element_text(size = 10),
        axis.title = element_text(size = 12), 
        legend.text = element_text(size = 12))

ggsave("../plots/03_max-lemmas_10-runs.png", plot = last_plot(),
       width = 8, height = 6, bg = "white", dpi = 300)
```

```{r}
runs_ranks %>% 
  ggplot(aes(x = run, y = max_lemma, group = author, colour = author)) +
    geom_bump(size = 1) +
    geom_point(size = 1) 
```

```{r}
ggplot(runs_ranks, aes(x = run, y = -rank, color = author)) +
  geom_bump(size = 1) +
  geom_point(size = 1)
```

All authors

```{r}
# add ranks by number of tokens
token_ranks <- corpus %>% 
  count(author, sort = T) %>% 
  mutate(rank_total = row_number()) %>% 
  select(-n) 

token_ranks
```

```{r}
# min corpus size is 5k tokens

x <- NULL
df <- NULL

for (i in 1:100) {
  x <- corpus %>% 
    group_by(author) %>% 
    sample_n(5000) %>% 
    ungroup() %>% 
    select(author, lemma) %>% 
    distinct() %>% 
    count(author, sort = T) %>% 
    mutate(rank = row_number(),
           run = i)
  
  df <- rbind(df, x)
}

glimpse(df)
```

```{r}
means <- df %>% 
  group_by(author) %>% 
  summarise(mean_n = mean(n))

df %>% 
  left_join(token_ranks, by = "author") %>% 
  left_join(means, by = "author") %>% 
  mutate(author_r = paste0(author, " (", rank_total, ")"),
         clr = ifelse(author == "Lermontov M.Ju.", "Our author", "Others")) %>% 
  ggplot(aes(x = reorder(author_r, -n, mean), y = n, fill = clr)) + 
  geom_boxplot() + 
  scale_fill_manual(values = c(met.brewer("Klimt")[1], 
                                  met.brewer("Java")[5])) + 
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(x = "Author (rank in total number of tokens)",
       y = "N types (lemmas)",
       fill = "")
```

```{r}
ranks_cor <- df %>% 
  group_by(author) %>% 
  summarise(mean_rank = mean(rank)) %>% 
  left_join(token_ranks, by = "author") 

cor(ranks_cor$mean_rank, ranks_cor$rank_total, method = "pearson") 
# correlation between rank in TTR sampling and in rank in terms of corpus size
```

Same run with 2k samples

```{r}
authors_10k

glimpse(corpus)

df <- NULL
x <- NULL

for (i in 1:100) {
  x <- corpus %>% 
    filter(author %in% authors_10k) %>% 
    group_by(author) %>% 
    sample_n(2000) %>% 
    select(author, word) %>% 
    distinct() %>% 
    count(sort = T) %>% 
    ungroup() %>% 
    mutate(run = i, 
           rank = row_number())
  
  df <- rbind(df, x)
}

df %>% sample_n(10)
```

Check how stable the number of unique words are

```{r}
df %>% 
  mutate(clr = ifelse(author == "Lermontov M.Ju.", "Our author", "Others")) %>% 
  ggplot(aes(x = run, y = n, group = author, colour = clr)) +
    geom_bump(size = 1, alpha = 0.6) +
    geom_point(size = 2, alpha = 0.6) + 
    scale_color_manual(values = c(met.brewer("Klimt")[1], 
                                  met.brewer("Java")[5])) + 
  labs(x = "Run", y = "Max number of lemmas", 
       colour = "", 
       title = "Number of unique words in 2,000 word samples",
       subtitle = "100 runs") + 
  scale_x_continuous(breaks = seq(1, 100, by = 1)) + 
  scale_y_continuous(breaks = seq(3000, 6000, by = 250)) + 
  theme(axis.text = element_text(size = 10),
        axis.title = element_text(size = 12), 
        legend.text = element_text(size = 12))
```

```{r}
df %>% 
  ggplot(aes(x = run, y = n, group = author, color = author)) + 
  geom_point() + geom_line()
```

Check ranks stability

```{r}
df %>% 
  mutate(author_cln = ifelse(author == "Lermontov M.Ju.", "Lerm", "Other")) %>% 
  ggplot(aes(x = run, y = -rank, color = author_cln)) +
  geom_bump(size = 1, alpha = 0.4) +
  geom_point(size = 1, alpha = 0.4)
```
