---
title: "02_keywords"
format: md
editor: visual
---

## Keywords analysis

## Load data & pckg

```{r, include=F, echo=F, message=F, warning=F}
library(tidyverse)
library(tidytext)
library(tidylo)
library(stylo)

library(MetBrewer)
library(cowplot)
theme_set(theme_minimal())
```

Load data

```{r, includ=T, echo=F}
# corpus with all words from ru-poetree by 20 authors
corpus <- read.csv("../data/large_poetree_ru_19c_lemma.csv") %>% select(-X)

# extract POS tags in a sep column
corpus <- corpus %>% 
  mutate(pos = str_extract(analysis, "gr': '.*?,"), 
         pos = str_remove_all(pos, "gr': '|=.*$|,"))

glimpse(corpus)
```

Kjetsaa's norm corpus replication:

```{r, include=T, echo=F}
# Kjetsaa's norm corpus replication
norm <- read.csv("../data/large_kjetsaa_norm.csv")

# create pos column
norm <- norm %>% 
  mutate(pos = str_extract(analysis, "gr': '.*?,"),
         pos = str_remove_all(pos, "gr': '|=.*$|,")) %>% 
  select(id, author_name, header, lemma, pos) %>% 
  mutate(corpus = "norm") %>% 
  rename(title = header,
         id_poem = id)

glimpse(norm)
```

### overview

Number of poems by 4 authors

```{r, include=T, echo=F}
corpus %>% 
  filter(author_name %in% c("Baratynskij E.A.",
                            "Lermontov M.Ju.",
                            "Fet A.A.",
                            "Tjutchev F.I."
                            )) %>% 
  select(author_name, id_poem) %>% 
  distinct() %>% 
  count(author_name, sort = T)
```

Number of words / lemmas

```{r, include=T, echo=F}
corpus %>%   
  filter(author_name %in% c("Baratynskij E.A.",
                            "Lermontov M.Ju.",
                            "Fet A.A.",
                            "Tjutchev F.I."
                            )) %>% 
  group_by(author_name) %>% 
  summarise(n_words = n(),
            n_lemmas = n_distinct(lemma),
            .groups = "drop")
```

Number of words in Kjetsaa's original authorial corpora:

-   Lermontov: 43 k

-   Baratynsky: 38 k

-   Tjutchev: 30 k

-   Fet: 36 k

## I. small corpus replication

## FN

```{r, include=F, echo=T}
# define pos tags
pos_key <- c("A", "S", "V")
```

Initialise functions to run the sampling for different measures

### Guiraud

```{r, echo=T}

# AUTHOR = author's name in Latin transcription, eg "Lermontov M.Ju."
# N_POEMS = limit number of poems in a sample, eg 270
# SAMPLE_SIZE = set number of tokens to sample (according to Kjetsaa's corpora or else), eg  43000

# CORPUS need to be set (lemmatized base corpus) + norm corpus loaded

# NORM should be either kjetsaa's one (no sampling) or calculated from the big corpus

guiraud_coeff <- function(AUTHOR, N_POEMS, SAMPLE_SIZE, NORM) {

  df <- NULL
  x <- NULL
  
  # for each pos
  for (pos_k in pos_key) {
    
    for (i in 1:100) {
  
      author_poems <- corpus %>% 
        filter(author_name == AUTHOR) %>% 
        select(id_poem) %>% 
        distinct() %>% 
        sample_n(N_POEMS) %>% 
        pull()
      
      # select lermontov bigger sample
      author_corpus <- corpus %>% 
        filter(author_name == AUTHOR) %>% 
        # filter selected 300 poems
        filter(id_poem %in% author_poems) %>% 
        select(id, author_name, title, lemma, pos) %>% 
        sample_n(SAMPLE_SIZE) %>% 
        mutate(corpus = AUTHOR)
      
      
      # calc freq in lermontov
      author_freq <- author_corpus %>% 
        filter(pos == pos_k) %>% 
        count(lemma, sort = T)
      
      if (NORM == "kjetsaa") {
        # freq in Kjetsaa's norm corpus
        norm_freq <- norm %>% 
          filter(pos == pos_k) %>% 
          count(lemma, sort = T) %>% 
          rename(norm_n = n) 
      } else {
        # create larger sampled norm (5k)
        norm_5k <- corpus %>% 
          group_by(author_name) %>% 
          sample_n(5000) %>% 
          ungroup() %>% 
          select(id, author_name, title, lemma, pos) %>% 
          mutate(corpus = "norm")
        
        # count_freqs
        norm_freq <- norm_5k %>% 
          filter(pos == pos_k) %>% 
          count(lemma, sort = T) %>% 
          rename(norm_n = n)
      }
      
      
      # join tables
      author_counts <- author_freq %>% 
        left_join(norm_freq, by = "lemma")
      
      # calculate theor freq & guiraud coeff, filter top-10
      x <- author_counts %>% 
        mutate(t = (norm_n * nrow(author_corpus))/nrow(author_corpus),
               diff = n - t,
               q = round(diff / sqrt(t), 2)) %>% 
        arrange(desc(q)) %>% 
        head(10) %>% 
        mutate(run = i,
               rank = row_number(),
               pos = pos_k)
      
      # append results
      df <- rbind(df, x)
    }
  }
  
  return(df)
}
```

### Log odds

```{r, echo=T}
log_odds_count <- function(AUTHOR, N_POEMS, SAMPLE_SIZE, NORM) {

  df <- tibble()
  x <- NULL
  
  for (pos_k in pos_key) {
    
    for (i in 1:100) {
  
        author_poems <- corpus %>% 
          filter(author_name == AUTHOR) %>% 
          select(id_poem) %>% 
          distinct() %>% 
          sample_n(N_POEMS) %>% 
          pull()
        
        # select lermontov bigger sample
        author_corpus <- corpus %>% 
          filter(author_name == AUTHOR) %>% 
          # filter selected 300 poems
          filter(id_poem %in% author_poems) %>% 
          # mutate(pos = str_extract(analysis, "gr': '.*?,"),
          #        pos = str_remove_all(pos, "gr': '|=.*$|,")) %>% 
          select(id, author_name, title, lemma, pos) %>% 
          # NB sample 43000 words! to make it similar to original selection
          sample_n(SAMPLE_SIZE) %>% 
          mutate(corpus = AUTHOR) %>% 
          rename(id_poem = id)
        
        
        if (NORM == "kjetsaa") {
          norm_corpus <- norm
        } else {
          norm_corpus <- corpus %>% 
            group_by(author_name) %>% 
            sample_n(5000) %>% 
            ungroup() %>% 
            select(id, author_name, title, lemma, pos) %>% 
            mutate(corpus = "norm") %>% 
            rename(id_poem = id)
        }
        
        author_norm <- rbind(author_corpus, norm_corpus)
      
        x <- author_norm %>% 
          filter(pos == pos_k) %>% 
          count(corpus, lemma, sort = T) %>% 
          bind_log_odds(corpus, lemma, n) %>% 
          arrange(-log_odds_weighted) %>% 
          group_by(corpus) %>% 
          slice_max(log_odds_weighted, n = 10) %>% 
          ungroup() %>% 
          filter(corpus == AUTHOR) %>% 
          head(10) %>% 
          mutate(run = i,
                 pos = pos_k)
      
        df <- rbind(df, x)
    }
  }
  return(df)
}
```

### Zeta

```{r, echo=T}
zeta_count <- function(AUTHOR, N_POEMS, SAMPLE_SIZE, NORM) {
  
  df <- NULL
  
  # fix wd as oppose() will mess with it
  stable_wd <- getwd()
  
  for (pos_k in pos_key) {
    
    for (i in 1:100) {
    # I. select random poems for lermontov
    
        author_poems <- corpus %>% 
          filter(author_name == AUTHOR) %>% 
          select(id_poem) %>% 
          distinct() %>% 
          sample_n(N_POEMS) %>% 
          pull()
        
        # select lermontov bigger sample
        author_corpus <- corpus %>% 
          filter(author_name == AUTHOR) %>% 
          # filter selected poems
          filter(id_poem %in% author_poems) %>% 
          # # create column with pos label
          # mutate(pos = str_extract(analysis, "gr': '.*?,"),
          #        pos = str_remove_all(pos, "gr': '|=.*$|,")) %>% 
          select(id, author_name, title, lemma, pos) %>% 
          
          # NB sample 43000 words! to make it similar to original selection
          sample_n(SAMPLE_SIZE) %>% 
          mutate(corpus = AUTHOR) %>% 
          rename(id_poem = id)
      
       if (NORM == "kjetsaa") {
          norm_corpus = norm
        } else {
          norm_corpus <- corpus %>% 
            group_by(author_name) %>% 
            sample_n(5000) %>% 
            ungroup() %>% 
            select(id, author_name, title, lemma, pos) %>% 
            mutate(corpus = "norm") %>% 
            rename(id_poem = id)
        }
        
      author_norm <- rbind(author_corpus, norm_corpus)
      
      # II. prepare corpus with samples
      corpus_prepared <- author_norm %>% 
        filter(pos == pos_k) %>% 
        group_by(corpus) %>% 
        sample_n(1000) %>% 
        mutate(sample_id = ceiling(1:1000),
               sample_id = floor(sample_id/500)+1, 
               sample_id = ifelse(sample_id == 3, 1, sample_id)) %>% 
        ungroup() %>% 
        mutate(sample_id = paste0(corpus, "_", sample_id)) %>% 
        group_by(sample_id) %>% 
        summarise(text = paste0(lemma, collapse = "  ")) %>% 
        mutate(corpus = str_remove(sample_id, "_\\d+$"), 
               path = ifelse(corpus == "norm", "secondary_set/", "primary_set/"),
               path = paste0("../data/zeta_tests/author_norm_00/", path, sample_id, ".txt"))
      
    
        # III. Remove old files & write new ones
        do.call(file.remove, list(
          list.files("../data/zeta_tests/author_norm_00//primary_set", full.names = TRUE)))
        
        do.call(file.remove, list(
          list.files("zeta_tests/author_norm_00//secondary_set", full.names = TRUE)))
        
        for (j in 1:nrow(corpus_prepared)) {
          writeLines(corpus_prepared$text[j], corpus_prepared$path[j])
        }
    
      # IV. run zeta
      oppose(
        gui = FALSE,
        path = "../data/zeta_tests/author_norm_00/",
        corpus.lang = "Other",
        text.slice.length = 250,
        write.png.file = TRUE
      )
    
      # return normal wd
      setwd(stable_wd)
      # read the results
      x <- readLines("~/Documents/github/kjetsaa/data/zeta_tests/author_norm_00/words_preferred.txt")
      x[8:17] # read top-10 words (first lines are comments to thelist)
    
      temp_df <- tibble(run = i,
                        pos = pos_k, 
                        words = paste(x[8:17], sep = " ", collapse = " "))
      
      df <- rbind(df, temp_df)
    } 
  } 
  
  df <- df %>% 
    separate_rows(words, sep = " ") %>% 
    rename(lemma = words)
  
  return(df)
} 
```

### calc intersection

```{r, echo=T}
calculate_intersection <- function(author_lists, results_df) {

  df_intersections <- tibble(pos = NULL,
                             run = NULL,
                             words = NULL,
                             n = NULL)
  # temp var
  x <- NULL
  
  for (j in 1:length(pos_key)) {
    
    pos_k <- pos_key[j]
    
    # extract the list of the keywords based on pos
    x <- author_lists %>% 
      filter(pos == pos_k) %>% 
      pull(text) %>% 
      str_split("\\n") %>% 
      unlist()
    
    # select only top-10 words
    x <- x[1:10]
  
    # temp results for this pos
    tmp <- tibble()
    
    # loop to iterate over new results & calc intersection
    for (i in 1:100) {
    
      wl <- results_df %>% 
        filter(run == i, pos == pos_k) %>% 
        pull(lemma) 
  
      w <- intersect(x, wl) # can later look which words exactly
      n <- length(w)
      
      tmp <- bind_rows(tmp, tibble(
        pos = pos_k,
        run = i,
        words = paste(w, collapse = " "),
        n = n
      ))
    }
    
    # append tmp results to the main table
    df_intersections <- bind_rows(df_intersections, tmp)
  }
  
  return(df_intersections)
} 
```

### plot

```{r, echo=F}
# simple pos translation table
pos_transl <- tibble(
  pos = c("A", "S", "V"),
  pos_tag = c("ADJ", "NOUN", "VERB")
)
```

```{r, echo=T}

plot_author <- function(guiraud_res, logodds_res, zeta_res) {
  
  # bind all intersection results together
  p1 <- guiraud_res %>% 
    mutate(group = "Guiraud\ncoeff.") %>% 
    rbind(logodds_res %>% mutate(group = "Weighted\nlog odds\nratio")) %>% 
    rbind(zeta_res %>% mutate(group = "Zeta")) %>% 
    # add pos labels
    left_join(pos_transl, by = "pos") %>% 
    # plot
    ggplot(aes(y = n, x = group, fill = group, colour = group)) + 
    geom_jitter(alpha = 0.5) + 
    geom_boxplot(alpha = 0.3) + 
    
    facet_wrap(~pos_tag, nrow = 3) + 
    labs(#y = "Number of words found in both lists", 
         #x = "Distinctiveness measure"
         y = "",
         x = "") + 
    scale_y_continuous(limits = c(-1, 10), 
                       breaks = seq(0, 10, by = 1)) + 
    scale_fill_manual(values = c(met.brewer("Java")[1],
                                 met.brewer("Java")[5],
                                 met.brewer("Java")[4])) + 
    
    scale_colour_manual(values = c(met.brewer("Java")[1],
                                 met.brewer("Java")[5],
                                 met.brewer("Java")[4])) +
    theme(legend.position = "None",
          axis.text = element_text(size = 16),
          axis.title = element_text(size = 18),
          strip.text = element_text(size = 18),
          #legend.text = element_text(size = 16), 
          #axis.line = element_line(colour = "black"),
          plot.title = element_text(size = 20),
          ) + 
    annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf)+
  annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf)
  return(p1)
}


```

## Lerm

Load lists of keywords for Lermontov

```{r, include=F, echo=T}
fl <- list.files(path = "../data/kjetsaa_lists/", 
                 pattern = "^1983_.*?_lerm.txt",
                 full.names = TRUE)

# read the list to a table
lerm_lists <- tibble(
  path = fl,
  author = "lerm",
  pos = str_remove_all(path, ".*?//1983_|_lerm\\.txt"),
  text = sapply(path, read_file)
)
```

```{r, include=T, echo=F}
# check lists if needed
lerm_ll <- lerm_lists %>% 
  pull(text) %>% 
  str_split("\\n") 

lerm_ll[[1]][1:10] # A
lerm_ll[[2]][1:10] # S
lerm_ll[[3]][1:10] # V
```

```{r, echo=T, include=T}
lerm_gr <- guiraud_coeff(AUTHOR = "Lermontov M.Ju.", 
                         N_POEMS = 270,
                         SAMPLE_SIZE = 43000,
                         NORM = "kjetsaa")

head(lerm_gr, 5)

# calculate intersections for Guiraud coeff
lerm_gr_int <- calculate_intersection(author_lists = lerm_lists, 
                                      results_df = lerm_gr)
head(lerm_gr_int)
```

```{r, echo=T, include=F}
lerm_lr <- log_odds_count(AUTHOR = "Lermontov M.Ju.",
                          N_POEMS = 280,
                          SAMPLE_SIZE = 43000,
                          NORM = "kjetsaa")

head(lerm_lr, 15)

lerm_lr_int <- calculate_intersection(author_lists = lerm_lists, 
                                      results_df = lerm_lr)

head(lerm_lr_int)
```

```{r, include=F, echo=F, message=F, warning=F}
lerm_zr <- zeta_count(AUTHOR = "Lermontov M.Ju.",
                      N_POEMS = 270,
                      SAMPLE_SIZE = 43000,
                      NORM = "kjetsaa")

head(lerm_zr)
tail(lerm_zr)

lerm_zr_int <- calculate_intersection(author_lists = lerm_lists, 
                                      results_df = lerm_zr)

head(lerm_lr_int)
```

Save the word lists

```{r, include=T, echo=T}
# create the outputs as 1 row = 1 word list (10 words)
# keep info about the author, measure, and POS

gr_wl <- lerm_gr %>% 
  mutate(measure = "Guiraud", 
         author = "Lermontov") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct() 

lr_wl <- lerm_lr %>% 
  mutate(measure = "Log odds",
         author = "Lermontov") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct()

zr_wl <- lerm_zr %>% 
  mutate(measure = "Zeta",
         author = "Lermontov") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct()

# merge the measures
lerm_wl <- rbind(gr_wl, lr_wl, zr_wl)

sample_n(lerm_wl, 3)

lerm_wl$word_list[3]
```

Create plots & store intersection data

```{r, include = T, echo=F}
plot_lerm <- plot_author(guiraud_res = lerm_gr_int, 
                         logodds_res = lerm_lr_int,
                         zeta_res = lerm_zr_int) + 
  labs(title = "Lermontov M.Ju.")


plot_lerm
```

```{r, echo = T, include = F}
x <- lerm_gr_int %>% 
    mutate(group = "Guiraud\ncoeff.") %>% 
    rbind(lerm_lr_int %>% mutate(group = "Weighted\nlog odds\nratio")) %>% 
    rbind(lerm_zr_int %>% mutate(group = "Zeta")) %>% 
    mutate(author = "Lermontov M.Ju.")

global_res <- NULL
global_res <- rbind(global_res, x)
```

```{r, echo = F}
rm(lerm_gr, lerm_lr, lerm_zr, x)
```

## Baratynsky

Load Kjetsaa's lists

```{r, include=F, echo=T}
fl <- list.files(path = "../data/kjetsaa_lists/", 
                 pattern = "^1983_.*?_bar.txt",
                 full.names = TRUE)

# read the list to a table
bar_lists <- tibble(
  path = fl,
  author = "bar",
  pos = str_remove_all(path, ".*?//1983_|_bar\\.txt"),
  text = sapply(path, read_file)
)

glimpse(bar_lists)
```

```{r, echo=T, include=F}
bar_gr <- guiraud_coeff(AUTHOR = "Baratynskij E.A.",
                        N_POEMS = 245,
                        SAMPLE_SIZE = 38000,
                        NORM = "kjetsaa"
                        )

head(bar_gr)

bar_gr_int <- calculate_intersection(author_lists =  bar_lists, 
                                     results_df = bar_gr)

bar_gr_int %>% sample_n(10)
```

```{r, echo=T, include=F}
bar_lr <- log_odds_count(AUTHOR = "Baratynskij E.A.",
                         N_POEMS = 245,
                         SAMPLE_SIZE = 38000,
                         NORM = "kjetsaa")

head(bar_lr)

bar_lr_int <- calculate_intersection(author_lists =  bar_lists, 
                                     results_df = bar_lr)

bar_lr_int %>% sample_n(10)
```

```{r, include=F, echo=T}
bar_zr <- zeta_count(AUTHOR = "Baratynskij E.A.",
                         N_POEMS = 245,
                         SAMPLE_SIZE = 38000,
                         NORM = "kjetsaa")

head(bar_zr)

bar_zr_int <- calculate_intersection(author_lists =  bar_lists, 
                                     results_df = bar_zr)

bar_zr_int %>% sample_n(10)
```

```{r, include=T, echo=F}
# create the outputs as 1 row = 1 word list (10 words)
# keep info about the author, measure, and POS

gr_wl <- bar_gr %>% 
  mutate(measure = "Guiraud", 
         author = "Baratynsky") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct() 

lr_wl <- bar_lr %>% 
  mutate(measure = "Log odds",
         author = "Baratynsky") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct()

zr_wl <- bar_zr %>% 
  mutate(measure = "Zeta",
         author = "Baratynsky") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct()

# merge the measures
bar_wl <- rbind(gr_wl, lr_wl, zr_wl)

sample_n(bar_wl, 3)

bar_wl$word_list[5]
```

```{r, include=T, echo=F}
plot_bar <- plot_author(guiraud_res = bar_gr_int, 
                         logodds_res = bar_lr_int,
                         zeta_res = bar_zr_int) + 
  labs(title = "Baratynskij E.A.")


plot_bar
```

```{r, echo=F, include=F}
x <- bar_gr_int %>% 
    mutate(group = "Guiraud\ncoeff.") %>% 
    rbind(bar_lr_int %>% mutate(group = "Weighted\nlog odds\nratio")) %>% 
    rbind(bar_zr_int %>% mutate(group = "Zeta")) %>% 
    mutate(author = "Baratynkij E.A.")

global_res <- rbind(global_res, x)
```

```{r, echo=F}
rm(bar_gr, bar_lr, bar_zr)
```

## Tjutchev

max n poems: 385

max n words: 33k

```{r, echo=T, include=F}
fl <- list.files(path = "../data/kjetsaa_lists/", 
                 pattern = "^1983_.*?_tjut.txt",
                 full.names = TRUE)

# read the list to a table
tjut_lists <- tibble(
  path = fl,
  author = "tjut",
  pos = str_remove_all(path, ".*?//1983_|_tjut\\.txt"),
  text = sapply(path, read_file)
)

glimpse(tjut_lists)
```

```{r, echo=T, include=F}
tjut_gr <- guiraud_coeff(AUTHOR = "Tjutchev F.I.",
                        N_POEMS = 385,
                        SAMPLE_SIZE = 33000,
                        NORM = "kjetsaa"
                        )

head(tjut_gr)

tjut_gr_int <- calculate_intersection(author_lists =  tjut_lists, 
                                     results_df = tjut_gr)

tjut_gr_int %>% sample_n(10)
```

```{r, echo=T, include=F}
tjut_lr <- log_odds_count(AUTHOR = "Tjutchev F.I.",
                          N_POEMS = 385,
                          SAMPLE_SIZE = 33000,
                          NORM = "kjetsaa")

head(tjut_lr)

tjut_lr_int <- calculate_intersection(author_lists = tjut_lists,
                                      results_df = tjut_lr)

head(tjut_lr_int)
```

```{r, echo=T, include=F, message=F, warning=F}
tjut_zr <- zeta_count(AUTHOR = "Tjutchev F.I.",
                      N_POEMS = 385,
                      SAMPLE_SIZE = 33000,
                      NORM = "kjetsaa")

head(tjut_zr)

tjut_zr_int <- calculate_intersection(author_lists = tjut_lists,
                                      results_df = tjut_zr)

head(tjut_zr_int)
```

```{r, include=T, echo=F}
# create the outputs as 1 row = 1 word list (10 words)
# keep info about the author, measure, and POS

gr_wl <- tjut_gr %>% 
  mutate(measure = "Guiraud", 
         author = "Tjutchev") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct() 

lr_wl <- tjut_lr %>% 
  mutate(measure = "Log odds",
         author = "Tjutchev") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct()

zr_wl <- tjut_zr %>% 
  mutate(measure = "Zeta",
         author = "Tjutchev") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct()

# merge the measures
tjut_wl <- rbind(gr_wl, lr_wl, zr_wl)

sample_n(tjut_wl, 3)

tjut_wl$word_list[5]
```

```{r, include=T, echo=F}
plot_tjut <- plot_author(guiraud_res = tjut_gr_int, 
                         logodds_res = tjut_lr_int,
                         zeta_res = tjut_zr_int) + 
  labs(title = "Tjutchev F.I.")


plot_tjut
```

```{r, include=F, echo=F}
x <- tjut_gr_int %>% 
    mutate(group = "Guiraud\ncoeff.") %>% 
    rbind(tjut_lr_int %>% mutate(group = "Weighted\nlog odds\nratio")) %>% 
    rbind(tjut_zr_int %>% mutate(group = "Zeta")) %>% 
    mutate(author = "Tjutchev F.I.")

global_res <- rbind(global_res, x)
```

```{r, echo=F}
rm(tjut_gr, tjut_lr, tjut_zr)
```

## Fet

max n poems : 920

max n words: 75k

Kjetsaa's corpus size: 36k

```{r, include=F, echo=F}
fl <- list.files(path = "../data/kjetsaa_lists/", 
                 pattern = "^1983_.*?_fet.txt",
                 full.names = TRUE)

# read the list to a table
fet_lists <- tibble(
  path = fl,
  author = "fet",
  pos = str_remove_all(path, ".*?//1983_|_fet\\.txt"),
  text = sapply(path, read_file)
)

glimpse(fet_lists)
```

```{r, include=F, echo=T}
fet_gr <- guiraud_coeff(AUTHOR = "Fet A.A.",
                        N_POEMS = 600,
                        SAMPLE_SIZE = 36000,
                         NORM = "kjetsaa")

fet_gr %>% sample_n(10)

fet_gr_int <- calculate_intersection(author_lists = fet_lists,
                                     results_df = fet_gr)
fet_gr_int %>% sample_n(10)
```

```{r, include=F, echo=T}
fet_lr <- log_odds_count(AUTHOR = "Fet A.A.",
                        N_POEMS = 600,
                        SAMPLE_SIZE = 36000,
                         NORM = "kjetsaa")

fet_lr %>% sample_n(10)

fet_lr_int <- calculate_intersection(author_lists = fet_lists,
                                     results_df = fet_lr)
fet_lr_int %>% sample_n(10)
```

```{r, include=F, echo=T}
fet_zr <- zeta_count(AUTHOR = "Fet A.A.",
                        N_POEMS = 600,
                        SAMPLE_SIZE = 36000,
                         NORM = "kjetsaa")

fet_zr %>% sample_n(10)

fet_zr_int <- calculate_intersection(author_lists = fet_lists,
                                     results_df = fet_zr)
fet_zr_int %>% sample_n(10)
```

```{r, include=T, echo=F}
# create the outputs as 1 row = 1 word list (10 words)
# keep info about the author, measure, and POS

gr_wl <- fet_gr %>% 
  mutate(measure = "Guiraud", 
         author = "Fet") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct() 

lr_wl <- fet_lr %>% 
  mutate(measure = "Log odds",
         author = "Fet") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct()

zr_wl <- fet_zr %>% 
  mutate(measure = "Zeta",
         author = "Fet") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct()

# merge the measures
fet_wl <- rbind(gr_wl, lr_wl, zr_wl)

sample_n(fet_wl, 3)

fet_wl$word_list[5]
```

```{r, include=T, echo=F}
plot_fet <- plot_author(guiraud_res = fet_gr_int, 
                         logodds_res = fet_lr_int,
                         zeta_res = fet_zr_int) + labs(title = "Fet A.A.")


plot_fet 
```

```{r, include=F, echo=F}
x <- fet_gr_int %>% 
    mutate(group = "Guiraud\ncoeff.") %>% 
    rbind(fet_lr_int %>% mutate(group = "Weighted\nlog odds\nratio")) %>% 
    rbind(fet_zr_int %>% mutate(group = "Zeta")) %>% 
    mutate(author = "Fet A.A.")

# save data on the intersections

global_res <- rbind(global_res, x)

saveRDS(global_res, file = "../data/keywords_res_kjetsaa_norm.rds")
```

```{r, include=F, echo=F}
# save the wordlists

global_wl <- rbind(lerm_wl,
                   bar_wl,
                   tjut_wl,
                   fet_wl) %>% 
  mutate(pos = ifelse(pos == "A", "ADJ", pos),
         pos = ifelse(pos == "V", "VERB", pos),
         pos = ifelse(pos == "S", "NOUN", pos))

global_wl %>% 
  count(author, measure, pos) # should be n (iter=word lists) = 100

sample_n(global_wl, 5)

write_csv(global_wl, "../data/kjetsaa_wordlists_kjetsaa-norm.csv")
```

## merge plot

```{r}
plot_grid(plot_lerm, plot_bar, plot_tjut, plot_fet,
          nrow = 1)

# ggsave(filename = "../plots/fig_3_kjetsaa_norm.png", 
#        plot = last_plot(), dpi = 300, bg = "white",
#        width = 15, height = 10)
```

## random lists

Output lists of randomly selected nouns, adj, and verbs

```{r}
lerm_pos <- corpus %>% 
  filter(author_name == "Lermontov M.Ju.") %>% 
  filter(pos %in% c("S", "V", "A")) %>% 
  group_by(pos) %>% 
  sample_n(size = 1000) %>% 
  mutate(sample_id = ceiling(row_number() / 10)) %>% 
  ungroup() %>% 
  select(author_name, lemma, pos, sample_id) %>% 
  group_by(pos, sample_id) %>% 
  mutate(word_list = paste(lemma, collapse = " ")) %>% 
  ungroup() %>% 
  select(-c(lemma)) %>% 
  distinct()

unique(corpus$author_name)

bar_pos <- corpus %>% 
  filter(author_name == "Baratynskij E.A.") %>% 
  filter(pos %in% c("S", "V", "A")) %>% 
  group_by(pos) %>% 
  sample_n(size = 1000) %>% 
  mutate(sample_id = ceiling(row_number() / 10)) %>% 
  ungroup() %>% 
  select(author_name, lemma, pos, sample_id) %>% 
  group_by(pos, sample_id) %>% 
  mutate(word_list = paste(lemma, collapse = " ")) %>% 
  ungroup() %>% 
  select(-c(lemma)) %>% 
  distinct()

tjut_pos <- corpus %>% 
  filter(author_name == "Tjutchev F.I.") %>% 
  filter(pos %in% c("S", "V", "A")) %>% 
  group_by(pos) %>% 
  sample_n(size = 1000) %>% 
  mutate(sample_id = ceiling(row_number() / 10)) %>% 
  ungroup() %>% 
  select(author_name, lemma, pos, sample_id) %>% 
  group_by(pos, sample_id) %>% 
  mutate(word_list = paste(lemma, collapse = " ")) %>% 
  ungroup() %>% 
  select(-c(lemma)) %>% 
  distinct()

fet_pos <- corpus %>% 
  filter(author_name == "Fet A.A.") %>% 
  filter(pos %in% c("S", "V", "A")) %>% 
  group_by(pos) %>% 
  sample_n(size = 1000) %>% 
  mutate(sample_id = ceiling(row_number() / 10)) %>% 
  ungroup() %>% 
  select(author_name, lemma, pos, sample_id) %>% 
  group_by(pos, sample_id) %>% 
  mutate(word_list = paste(lemma, collapse = " ")) %>% 
  ungroup() %>% 
  select(-c(lemma)) %>% 
  distinct()

random_lists <- rbind(lerm_pos,
                      bar_pos,
                      tjut_pos, 
                      fet_pos) 

  # simple pos translation table
pos_transl <- tibble(
  pos = c("A", "S", "V"),
  pos_tag = c("ADJ", "NOUN", "VERB")
)


random_lists <- random_lists %>% 
  left_join(pos_transl, by = "pos") %>% 
  select(-pos) %>% 
  rename(pos = pos_tag, 
         run = sample_id,
         author = author_name) %>% 
  select(author, run, pos, word_list)

head(random_lists)

random_lists %>% 
  count(pos, author)

write_csv(random_lists, "../data/random_lists.csv")
```

## analyse keywords

```{r, echo=F, eval=F}
res_k <- readRDS("../data/keywords_res_kjetsaa_norm.rds")

glimpse(res_k)
```

N words of different pos in 4 authors & top-freq words

```{r, echo=F, eval=F}
corpus %>% 
  filter(author_name %in% c("Lermontov M.Ju.", "Baratynskij E.A.",
                            "Tjutchev F.I.", "Fet A.A.")) %>% 
  filter(pos %in% c("A", "S", "V")) %>% 
  count(author_name, pos)
```

```{r, echo=F, eval=F}
freq_l <- corpus %>% 
  filter(author_name %in% c("Lermontov M.Ju.")) %>% 
  filter(pos %in% c("A", "S", "V")) %>% 
  group_by(pos) %>% 
  count(lemma, sort = T) %>% 
  slice_max(order_by = n, n = 10)

key_l <- res_k %>% 
  filter(author == "Lermontov M.Ju." & words != "") %>% 
  separate_rows(words, sep = " ") %>% 
  group_by(pos) %>% 
  count(words, sort = T) 

intersect(freq_l$lemma, key_l$words)

res_k %>% 
  filter(author == "Lermontov M.Ju." & words != "") %>% 
  filter(group == "Guiraud\ncoeff.") %>% 
  separate_rows(words, sep = " ") %>% 
  count(words, pos, sort = T) %>% 
  arrange(-desc(pos))

res_k %>% 
  filter(author == "Lermontov M.Ju." & words != "") %>% 
  filter(group == "Weighted\nlog odds\nratio") %>% 
  separate_rows(words, sep = " ") %>% 
  count(words, pos, sort = T) %>% 
  arrange(-desc(pos))

res_k %>% 
  filter(author == "Lermontov M.Ju." & words != "") %>% 
  filter(group == "Zeta") %>% 
  separate_rows(words, sep = " ") %>% 
  count(words, pos, sort = T) %>% 
  arrange(-desc(pos))
```

```{r, echo=F, eval=F}
freq_b <- corpus %>% 
  filter(author_name %in% c("Baratynskij E.A.")) %>% 
  filter(pos %in% c("A", "S", "V")) %>% 
  group_by(pos) %>% 
  count(lemma, sort = T) %>% 
  slice_max(order_by = n, n = 10)

key_b <- res_k %>% 
  filter(author == "Baratynkij E.A." & words != "") %>% 
  separate_rows(words, sep = " ") %>% 
  group_by(pos) %>% 
  count(words, sort = T) 

intersect(freq_b$lemma, key_b$words)

res_k %>% 
  filter(author == "Baratynkij E.A." & words != "") %>% 
  filter(group == "Guiraud\ncoeff.") %>% 
  separate_rows(words, sep = " ") %>% 
  count(words, pos, sort = T) %>% 
  arrange(-desc(pos))

res_k %>% 
  filter(author == "Baratynkij E.A." & words != "") %>% 
  filter(group == "Weighted\nlog odds\nratio") %>% 
  separate_rows(words, sep = " ") %>% 
  count(words, pos, sort = T) %>% 
  arrange(-desc(pos))

res_k %>% 
  filter(author == "Baratynkij E.A." & words != "") %>% 
  filter(group == "Zeta") %>% 
  separate_rows(words, sep = " ") %>% 
  count(words, pos, sort = T) %>% 
  arrange(-desc(pos))
```

```{r, echo=F, eval=F}
freq_t <- corpus %>% 
  filter(author_name %in% c("Tjutchev F.I.")) %>% 
  filter(pos %in% c("A", "S", "V")) %>% 
  group_by(pos) %>% 
  count(lemma, sort = T) %>% 
  slice_max(order_by = n, n = 10)

key_t <- res_k %>% 
  filter(author == "Tjutchev F.I." & words != "") %>% 
  separate_rows(words, sep = " ") %>% 
  group_by(pos) %>% 
  count(words, sort = T) 

intersect(freq_t$lemma, key_t$words)

res_k %>% 
  filter(author == "Tjutchev F.I." & words != "") %>% 
  filter(group == "Guiraud\ncoeff.") %>% 
  separate_rows(words, sep = " ") %>% 
  count(words, pos, sort = T) %>% 
  arrange(-desc(pos))

res_k %>% 
  filter(author == "Tjutchev F.I." & words != "") %>% 
  filter(group == "Weighted\nlog odds\nratio") %>% 
  separate_rows(words, sep = " ") %>% 
  count(words, pos, sort = T) %>% 
  arrange(-desc(pos))

res_k %>% 
  filter(author == "Tjutchev F.I." & words != "") %>% 
  filter(group == "Zeta") %>% 
  separate_rows(words, sep = " ") %>% 
  count(words, pos, sort = T) %>% 
  arrange(-desc(pos))
```

```{r, echo=F, eval=F}
freq_f <- corpus %>% 
  filter(author_name %in% c("Fet A.A.")) %>% 
  filter(pos %in% c("A", "S", "V")) %>% 
  group_by(pos) %>% 
  count(lemma, sort = T) %>% 
  slice_max(order_by = n, n = 10)

key_f <- res_k %>% 
  filter(author == "Fet A.A." & words != "") %>% 
  separate_rows(words, sep = " ") %>% 
  group_by(pos) %>% 
  count(words, sort = T) 

intersect(freq_f$lemma, key_f$words)

res_k %>% 
  filter(author == "Fet A.A." & words != "") %>% 
  filter(group == "Guiraud\ncoeff.") %>% 
  separate_rows(words, sep = " ") %>% 
  count(words, pos, sort = T) %>% 
  arrange(-desc(pos))

res_k %>% 
  filter(author == "Fet A.A." & words != "") %>% 
  filter(group == "Weighted\nlog odds\nratio") %>% 
  separate_rows(words, sep = " ") %>% 
  count(words, pos, sort = T) %>% 
  arrange(-desc(pos))

res_k %>% 
  filter(author == "Fet A.A." & words != "") %>% 
  filter(group == "Zeta") %>% 
  separate_rows(words, sep = " ") %>% 
  count(words, pos, sort = T) %>% 
  arrange(-desc(pos))
```

# II. 5k norm

Same experiment with a larger contrast corpus

### Lerm

```{r, include=F, echo=T}
# LERMONTOV

lerm_gr <- guiraud_coeff(AUTHOR = "Lermontov M.Ju.", 
                         N_POEMS = 270,
                         SAMPLE_SIZE = 43000,
                         NORM = "5k")

# calculate intersections for Guiraud coeff
lerm_gr_int <- calculate_intersection(author_lists = lerm_lists, 
                                      results_df = lerm_gr)
```

```{r, include=F, echo=T}
lerm_lr <- log_odds_count(AUTHOR = "Lermontov M.Ju.",
                          N_POEMS = 270,
                          SAMPLE_SIZE = 43000,
                          NORM = "5k")

lerm_lr_int <- calculate_intersection(author_lists = lerm_lists, 
                                      results_df = lerm_lr)
```

```{r, include=F, echo=T, message=F, warning=F}
lerm_zr <- zeta_count(AUTHOR = "Lermontov M.Ju.",
                      N_POEMS = 270,
                      SAMPLE_SIZE = 43000,
                      NORM = "5k")
head(lerm_zr)

lerm_zr_int <- calculate_intersection(author_lists = lerm_lists, 
                                      results_df = lerm_zr)
```

```{r, include=T, echo=T}
# create the outputs as 1 row = 1 word list (10 words)
# keep info about the author, measure, and POS

gr_wl <- lerm_gr %>% 
  mutate(measure = "Guiraud", 
         author = "Lermontov") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct() 

lr_wl <- lerm_lr %>% 
  mutate(measure = "Log odds",
         author = "Lermontov") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct()

zr_wl <- lerm_zr %>% 
  mutate(measure = "Zeta",
         author = "Lermontov") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct()

# merge the measures
lerm_wl <- rbind(gr_wl, lr_wl, zr_wl)

sample_n(lerm_wl, 3)

lerm_wl$word_list[3]
```

```{r, include=T, echo=F}
plot_lerm <- plot_author(guiraud_res = lerm_gr_int, 
                         logodds_res = lerm_lr_int,
                         zeta_res = lerm_zr_int) + 
  labs(title = "Lermontov M.Ju.")


plot_lerm
```

```{r, include=F, echo=F}
x <- lerm_gr_int %>% 
    mutate(group = "Guiraud\ncoeff.") %>% 
    rbind(lerm_lr_int %>% mutate(group = "Weighted\nlog odds\nratio")) %>% 
    rbind(lerm_zr_int %>% mutate(group = "Zeta")) %>% 
    mutate(author = "Lermontov M.Ju.")

global_res <- NULL
global_res <- rbind(global_res, x)

rm(lerm_gr, lerm_lr, lerm_zr, x)
```

### Baratynsky

```{r, include=F, echo=T}
bar_gr <- guiraud_coeff(AUTHOR = "Baratynskij E.A.",
                        N_POEMS = 245,
                        SAMPLE_SIZE = 38000,
                        NORM = "5k"
                        )

bar_gr_int <- calculate_intersection(author_lists =  bar_lists, 
                                     results_df = bar_gr)
```

```{r, include=F, echo=T}
bar_lr <- log_odds_count(AUTHOR = "Baratynskij E.A.",
                         N_POEMS = 245,
                         SAMPLE_SIZE = 38000,
                         NORM = "5k")

bar_lr_int <- calculate_intersection(author_lists =  bar_lists, 
                                     results_df = bar_lr)
```

```{r, include=F, echo=T, message=FALSE, warning=FALSE}
bar_zr <- zeta_count(AUTHOR = "Baratynskij E.A.",
                         N_POEMS = 245,
                         SAMPLE_SIZE = 38000,
                         NORM = "5k")

bar_zr_int <- calculate_intersection(author_lists =  bar_lists, 
                                     results_df = bar_zr)
```

```{r, include=T, echo=F}
# create the outputs as 1 row = 1 word list (10 words)
# keep info about the author, measure, and POS

gr_wl <- bar_gr %>% 
  mutate(measure = "Guiraud", 
         author = "Baratynsky") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct() 

lr_wl <- bar_lr %>% 
  mutate(measure = "Log odds",
         author = "Baratynsky") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct()

zr_wl <- bar_zr %>% 
  mutate(measure = "Zeta",
         author = "Baratynsky") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct()

# merge the measures
bar_wl <- rbind(gr_wl, lr_wl, zr_wl)

sample_n(bar_wl, 3)

bar_wl$word_list[5]
```

```{r, include=T, echo=F}
plot_bar <- plot_author(guiraud_res = bar_gr_int, 
                         logodds_res = bar_lr_int,
                         zeta_res = bar_zr_int) + 
  labs(title = "Baratynskij E.A.")


plot_bar
```

```{r, include=F, echo=F}
x <- bar_gr_int %>% 
    mutate(group = "Guiraud\ncoeff.") %>% 
    rbind(bar_lr_int %>% mutate(group = "Weighted\nlog odds\nratio")) %>% 
    rbind(bar_zr_int %>% mutate(group = "Zeta")) %>% 
    mutate(author = "Baratynkij E.A.")

global_res <- rbind(global_res, x)

rm(bar_gr, bar_lr, bar_zr)
```

### Tjut

```{r, include=F, echo=T}
tjut_gr <- guiraud_coeff(AUTHOR = "Tjutchev F.I.",
                        N_POEMS = 385,
                        SAMPLE_SIZE = 33000,
                        NORM = "5k"
                        )

tjut_gr_int <- calculate_intersection(author_lists =  tjut_lists, 
                                     results_df = tjut_gr)
```

```{r, include=F, echo=T}
tjut_lr <- log_odds_count(AUTHOR = "Tjutchev F.I.",
                          N_POEMS = 385,
                          SAMPLE_SIZE = 33000,
                          NORM = "5k")

tjut_lr_int <- calculate_intersection(author_lists = tjut_lists,
                                      results_df = tjut_lr)
```

```{r, include=F, echo=T, message=F, warning=F}
tjut_zr <- zeta_count(AUTHOR = "Tjutchev F.I.",
                      N_POEMS = 385,
                      SAMPLE_SIZE = 33000,
                      NORM = "5k")

tjut_zr_int <- calculate_intersection(author_lists = tjut_lists,
                                      results_df = tjut_zr)
```

```{r, include=F, echo=F}
# create the outputs as 1 row = 1 word list (10 words)
# keep info about the author, measure, and POS

gr_wl <- tjut_gr %>% 
  mutate(measure = "Guiraud", 
         author = "Tjutchev") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct() 

lr_wl <- tjut_lr %>% 
  mutate(measure = "Log odds",
         author = "Tjutchev") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct()

zr_wl <- tjut_zr %>% 
  mutate(measure = "Zeta",
         author = "Tjutchev") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct()

# merge the measures
tjut_wl <- rbind(gr_wl, lr_wl, zr_wl)

sample_n(tjut_wl, 3)

tjut_wl$word_list[5]

```

```{r, include=T, echo=F}
plot_tjut <- plot_author(guiraud_res = tjut_gr_int, 
                         logodds_res = tjut_lr_int,
                         zeta_res = tjut_zr_int) + 
  labs(title = "Tjutchev F.I.")


plot_tjut
```

```{r, include=F, echo=F}
x <- tjut_gr_int %>% 
    mutate(group = "Guiraud\ncoeff.") %>% 
    rbind(tjut_lr_int %>% mutate(group = "Weighted\nlog odds\nratio")) %>% 
    rbind(tjut_zr_int %>% mutate(group = "Zeta")) %>% 
    mutate(author = "Tjutchev F.I.")

global_res <- rbind(global_res, x)

rm(tjut_gr, tjut_lr, tjut_zr)
```

### Fet

```{r, include=F, echo=T}
fet_gr <- guiraud_coeff(AUTHOR = "Fet A.A.",
                        N_POEMS = 600,
                        SAMPLE_SIZE = 36000,
                         NORM = "5k")

fet_gr_int <- calculate_intersection(author_lists = fet_lists,
                                     results_df = fet_gr)
```

```{r, include=F, echo = T}
fet_lr <- log_odds_count(AUTHOR = "Fet A.A.",
                        N_POEMS = 600,
                        SAMPLE_SIZE = 36000,
                         NORM = "5k")

fet_lr_int <- calculate_intersection(author_lists = fet_lists,
                                     results_df = fet_lr)
```

```{r, include=F, echo=T, warning=F, message=F}
fet_zr <- zeta_count(AUTHOR = "Fet A.A.",
                        N_POEMS = 600,
                        SAMPLE_SIZE = 36000,
                         NORM = "5k")

fet_zr_int <- calculate_intersection(author_lists = fet_lists,
                                     results_df = fet_zr)
```

```{r, include=T, echo=F}
# create the outputs as 1 row = 1 word list (10 words)
# keep info about the author, measure, and POS

gr_wl <- fet_gr %>% 
  mutate(measure = "Guiraud", 
         author = "Fet") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct() 

lr_wl <- fet_lr %>% 
  mutate(measure = "Log odds",
         author = "Fet") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct()

zr_wl <- fet_zr %>% 
  mutate(measure = "Zeta",
         author = "Fet") %>% 
  select(author, measure, run, pos, lemma) %>% 
  group_by(author, measure, run, pos) %>% 
  summarise(word_list = paste(lemma, collapse = " "),
            .groups = "drop") %>% 
  distinct()

# merge the measures
fet_wl <- rbind(gr_wl, lr_wl, zr_wl)

sample_n(fet_wl, 3)

fet_wl$word_list[5]
```

```{r, include=T, echo=F}
plot_fet <- plot_author(guiraud_res = fet_gr_int, 
                         logodds_res = fet_lr_int,
                         zeta_res = fet_zr_int) + labs(title = "Fet A.A.")


plot_fet 
```

```{r, include=F, echo=F}
x <- fet_gr_int %>% 
    mutate(group = "Guiraud\ncoeff.") %>% 
    rbind(fet_lr_int %>% mutate(group = "Weighted\nlog odds\nratio")) %>% 
    rbind(fet_zr_int %>% mutate(group = "Zeta")) %>% 
    mutate(author = "Fet A.A.")

global_res <- rbind(global_res, x)

saveRDS(global_res, file = "../data/keywords_res_5k_norm.rds")
```

```{r, include=F, echo=F}
# save the wordlists

global_wl <- rbind(lerm_wl,
                   bar_wl,
                   tjut_wl,
                   fet_wl) %>% 
  mutate(pos = ifelse(pos == "A", "ADJ", pos),
         pos = ifelse(pos == "V", "VERB", pos),
         pos = ifelse(pos == "S", "NOUN", pos))

global_wl %>% 
  count(author, measure, pos) # should be n (iter=word lists) = 100

sample_n(global_wl, 5)

# write_csv(global_wl, "../data/kjetsaa_wordlists_5k.csv")
```

### merged plot

```{r, include=T, echo=F}
plot_grid(plot_lerm, plot_bar, plot_tjut, plot_fet,
          nrow = 1)

# ggsave(filename = "../plots/fig_3_5k_norm.png", 
#        plot = last_plot(), dpi = 300, bg = "white",
#        width = 15, height = 10)
```
