---
title: "02_keywords"
format: html
editor: visual
---

## Keywords analysis

## Load data & pckg

```{r}
library(tidyverse)
library(tidytext)
library(tidylo)
library(stylo)

library(MetBrewer)
theme_set(theme_minimal())
```

```{r}
# corpus with all words from ru-poetree by 20 authors
corpus <- read.csv("../data/poetree_ru_19c_lemma.csv") %>% select(-X)

glimpse(corpus)
```

```{r}
norm <- read.csv("../data/kjetsaa_norm_lemma.csv") %>% select(-X)
glimpse(norm)
```

## I. small corpus replication

```{r}
lerm_poems <- corpus %>% 
  filter(author_name == "Lermontov M.Ju.") %>% 
  select(id_poem) %>% 
  distinct() %>% 
  sample_n(170) %>% 
  pull()

# select lermontov bigger sample
lerm <- corpus %>% 
  filter(author_name == "Lermontov M.Ju.") %>% 
  # filter selected 150 poems
  filter(id_poem %in% lerm_poems) %>% 
  
  mutate(pos = str_extract(analysis, "gr': '.*?,"),
         pos = str_remove_all(pos, "gr': '|=.*$|,")) %>% 
  select(id_poem, author_name, title, lemma, pos) %>% 
  
  # NB sample 43000 words! to make it similar to original selection
  # sample_n(43000) %>% 
  mutate(corpus = "lerm")

glimpse(lerm)
```

Prepare 'norm' corpus for comparison

```{r}
norm <- norm %>% 
  mutate(pos = str_extract(analysis, "gr': '.*?,"),
         pos = str_remove_all(pos, "gr': '|=.*$|,")) %>% 
  select(id, author_name, header, lemma, pos) %>% 
  mutate(corpus = "norm") %>% 
  rename(title = header,
         id_poem = id)

glimpse(norm)
```

```{r}
colnames(lerm) == colnames(norm)

lerm_norm <- rbind(lerm, norm)
```

### base adj freq

MF adj in Lerm & in norm

```{r}
x <- lerm %>% 
  filter(pos == "A") %>% nrow() # number of adjectives

lerm %>% 
  filter(pos == "A") %>% 
  count(lemma, sort = T) %>% 
  mutate(perc = round(n/x * 100, 2 ))
```

```{r}
x <- norm %>% 
  filter(pos == "A") %>% nrow() # number of adjectives

norm %>% 
  filter(pos == "A") %>% 
  count(lemma, sort = T) %>% 
  mutate(perc = round(n/x * 100, 2 ))
```

```{r}
lerm %>% select(title) %>% distinct()
norm %>% select(title) %>% distinct()
```

### Giuraud coeff

```{r}
lerm_freq <- lerm %>% 
  filter(pos == "A") %>% 
  count(lemma, sort = T)

norm_freq <- norm %>% 
  filter(pos == "A") %>% 
  count(lemma, sort = T) %>% 
  rename(norm_n = n) 

lerm_counts <- lerm_freq %>% 
  left_join(norm_freq, by = "lemma")

lerm_counts %>% 
  mutate(t = (norm_n * nrow(lerm))/nrow(norm),
         diff = n - t,
         q = round(diff / sqrt(t), 2)) %>% 
  arrange(desc(q)) %>% 
  head(20)
```

#### sampled (10 runs)

```{r}
# repeated
# norm <- norm %>% 
#   mutate(pos = str_extract(analysis, "gr': '.*?,"),
#          pos = str_remove_all(pos, "gr': '|=.*$|,")) %>% 
#   select(id, author, header, lemma, pos) %>% 
#   mutate(corpus = "norm")

glimpse(norm)

unique(norm$pos)
```

## FN

```{r}
# define pos tags
pos_key <- c("A", "S", "V")
```

Functions to run the sampling for different measures

### Guiraud

```{r}

# AUTHOR = author's name in Latin transcription, eg "Lermontov M.Ju."
# N_POEMS = limit number of poems in a sample, eg 270
# SAMPLE_SIZE = set number of tokens to sample (according to Kjetsaa's corpora or else), eg  43000

# CORPUS need to be set (lemmatized base corpus) + norm corpus loaded

guiraud_coeff <- function(AUTHOR, N_POEMS, SAMPLE_SIZE) {

  df <- NULL
  x <- NULL
  
  # for each pos
  for (pos_k in pos_key) {
    
    for (i in 1:100) {
  
      author_poems <- corpus %>% 
        filter(author_name == AUTHOR) %>% 
        # select small poems
        # filter(verses < 257) %>% 
        select(title) %>% 
        distinct() %>% 
        sample_n(N_POEMS) %>% 
        pull()
      
      # select lermontov bigger sample
      author_corpus <- corpus %>% 
        filter(author_name == AUTHOR) %>% 
        # filter selected 300 poems
        filter(title %in% author_poems) %>% 
        
        mutate(pos = str_extract(analysis, "gr': '.*?,"),
               pos = str_remove_all(pos, "gr': '|=.*$|,")) %>% 
        select(id, author_name, title, lemma, pos) %>% 
        
        sample_n(SAMPLE_SIZE) %>% 
        mutate(corpus = AUTHOR)
      
      
      # calc freq in lermontov
      author_freq <- author_corpus %>% 
        filter(pos == pos_k) %>% 
        count(lemma, sort = T)
      
      # freq in norm corpus
      norm_freq <- norm %>% 
        filter(pos == pos_k) %>% 
        count(lemma, sort = T) %>% 
        rename(norm_n = n) 
      
      # join tables
      author_counts <- author_freq %>% 
        left_join(norm_freq, by = "lemma")
      
      # calculate theor freq & guiraud coeff, filter top-10
      x <- author_counts %>% 
        mutate(t = (norm_n * nrow(author_corpus))/nrow(author_corpus),
               diff = n - t,
               q = round(diff / sqrt(t), 2)) %>% 
        arrange(desc(q)) %>% 
        head(10) %>% 
        mutate(run = i,
               rank = row_number(),
               pos_k = pos_x)
      
      # append results
      df <- rbind(df, x)
    }
  }
  
  return(df)
}
```

### Lerm 

```{r}

df <- tibble()
x <- NULL

pos_key <- c("A", "S", "V")

for (pos_x in pos_key) {
  
  for (i in 1:100) {

    lerm_poems <- corpus %>% 
      filter(author_name == "Lermontov M.Ju.") %>% 
      # select small poems
      # filter(verses < 257) %>% 
      select(title) %>% 
      distinct() %>% 
      sample_n(270) %>% 
      pull()
    
    # select lermontov bigger sample
    lerm <- corpus %>% 
      filter(author_name == "Lermontov M.Ju.") %>% 
      # filter selected 300 poems
      filter(title %in% lerm_poems) %>% 
      
      mutate(pos = str_extract(analysis, "gr': '.*?,"),
             pos = str_remove_all(pos, "gr': '|=.*$|,")) %>% 
      select(id, author_name, title, lemma, pos) %>% 
      
      # NB sample 43000 words! to make it similar to original selection
      sample_n(43000) %>% 
      mutate(corpus = "lerm")
    
    # glimpse(lerm)
    
    # calc freq in lermontov
    lerm_freq <- lerm %>% 
      filter(pos == pos_x) %>% 
      count(lemma, sort = T)
    
    # freq in norm corpus
    norm_freq <- norm %>% 
      filter(pos == pos_x) %>% 
      count(lemma, sort = T) %>% 
      rename(norm_n = n) 
    
    # join tables
    lerm_counts <- lerm_freq %>% 
      left_join(norm_freq, by = "lemma")
    
    # calculate theor freq & guiraud coeff, filter top-10
    x <- lerm_counts %>% 
      mutate(t = (norm_n * nrow(lerm))/nrow(norm),
             diff = n - t,
             q = round(diff / sqrt(t), 2)) %>% 
      arrange(desc(q)) %>% 
      head(10) %>% 
      mutate(run = i,
             rank = row_number(),
             pos_k = pos_x)
    
    # append results
    df <- rbind(df, x)
  }
}

df %>% head(20)
df %>% sample_n(10)

df <- df %>% 
  rename(pos = pos_k)

glimpse(df)
```

Load Kjetsaa's lists and calculate intersection

```{r}
fl <- list.files(path = "../data/kjetsaa_lists/", 
                 pattern = "^1983_.*?_lerm.txt",
                 full.names = TRUE)

# read the list to a table
lerm_lists <- tibble(
  path = fl,
  author = "lerm",
  pos = str_remove_all(path, ".*?//1983_|_lerm\\.txt"),
  text = sapply(path, read_file)
)

# save just the word vectors, only the first 10 elements
lerm_ll <- lerm_lists %>% 
  pull(text) %>% 
  str_split("\\n") 

lerm_adj <- lerm_ll[[1]][1:10]
lerm_nouns <- lerm_ll[[2]][1:10]
lerm_verbs <- lerm_ll[[3]][1:10]

cat("ADJ:", lerm_adj, "\nNOUNS:", lerm_nouns, "\nVERBS:", lerm_verbs)
```

Calculate number of intersections

```{r}

df_intersections <- tibble(pos = NULL,
                           run = NULL,
                           words = NULL,
                           n = NULL)
# temp var
x <- NULL

for (j in 1:length(pos_key)) {
  
  pos_k <- pos_key[j]
  
  # extract the list of the keywords based on pos
  x <- lerm_lists %>% 
    filter(pos == pos_k) %>% 
    pull(text) %>% 
    str_split("\\n") %>% 
    unlist()
  
  # select only top-10 words
  x <- x[1:10]

  # temp results for this pos
  tmp <- tibble()
  
  # loop to iterate over new results & calc intersection
  for (i in 1:100) {
  
    wl <- df %>% 
      filter(run == i, pos == pos_k) %>% 
      pull(lemma) 

    w <- intersect(x, wl) # can later look which words exactly
    n <- length(w)
    
    tmp <- bind_rows(tmp, tibble(
      pos = pos_k,
      run = i,
      words = paste(w, collapse = " "),
      n = n
    ))
  }
  
  # append tmp results to the main table
  df_intersections <- bind_rows(df_intersections, tmp)
}


lerm_gr <- df_intersections

glimpse(lerm_gr)
```

```{r}
# calculate n times a word was in intersection of the two lists
lerm_gr %>% 
  unnest_tokens(input = "words", output = word, token = "words") %>% 
  count(word, sort = T)
```

### log odds

```{r}
# test run with one list of words
lerm_norm %>% 
  filter(pos == "A") %>% 
  count(corpus, lemma, sort = T) %>% 
  bind_log_odds(corpus, lemma, n) %>% 
  arrange(-log_odds_weighted) %>% 
  group_by(corpus) %>% 
  slice_max(log_odds_weighted, n = 10) %>% 
  ungroup() %>% 
  mutate(lemma = reorder(lemma, log_odds_weighted)) %>% 
  ggplot(aes(x = log_odds_weighted, y = lemma, fill = corpus)) + 
  geom_col() + 
  facet_wrap(~corpus, scales = "free") + 
  labs(y = NULL)
```

```{r}
df <- tibble()
x <- NULL

for (pos_k in pos_key) {
  
  for (i in 1:100) {

    lerm_poems <- corpus %>% 
        filter(author_name == "Lermontov M.Ju.") %>% 
        # select small poems
        # filter(verses < 257) %>% 
        select(title) %>% 
        distinct() %>% 
        sample_n(270) %>% 
        pull()
      
      # select lermontov bigger sample
      lerm <- corpus %>% 
        filter(author_name == "Lermontov M.Ju.") %>% 
        # filter selected 300 poems
        filter(title %in% lerm_poems) %>% 
        
        mutate(pos = str_extract(analysis, "gr': '.*?,"),
               pos = str_remove_all(pos, "gr': '|=.*$|,")) %>% 
        select(id, author_name, title, lemma, pos) %>% 
        
        # NB sample 43000 words! to make it similar to original selection
        sample_n(43000) %>% 
        mutate(corpus = "lerm") %>% 
        rename(id_poem = id)
    
      # glimpse(lerm)
      lerm_norm <- rbind(lerm, norm)
    
      x <- lerm_norm %>% 
        filter(pos == pos_k) %>% 
        count(corpus, lemma, sort = T) %>% 
        bind_log_odds(corpus, lemma, n) %>% 
        arrange(-log_odds_weighted) %>% 
        group_by(corpus) %>% 
        slice_max(log_odds_weighted, n = 10) %>% 
        ungroup() %>% 
        filter(corpus == "lerm") %>% 
        head(10) %>% 
        mutate(run = i,
               pos = pos_k)
    
      df <- rbind(df, x)
  }
  
}


df %>% sample_n(10)
```

```{r}
df_intersections <- tibble(pos = NULL,
                           run = NULL,
                           words = NULL,
                           n = NULL)
# temp var
x <- NULL

for (j in 1:length(pos_key)) {
  
  pos_k <- pos_key[j]
  
  # extract the list of the keywords based on pos
  x <- lerm_lists %>% 
    filter(pos == pos_k) %>% 
    pull(text) %>% 
    str_split("\\n") %>% 
    unlist()
  
  # select only top-10 words
  x <- x[1:10]

  # temp results for this pos
  tmp <- tibble()
  
  # loop to iterate over new results & calc intersection
  for (i in 1:100) {
  
    wl <- df %>% 
      filter(run == i, pos == pos_k) %>% 
      pull(lemma) 

    w <- intersect(x, wl) # can later look which words exactly
    n <- length(w)
    
    tmp <- bind_rows(tmp, tibble(
      pos = pos_k,
      run = i,
      words = paste(w, collapse = " "),
      n = n
    ))
  }
  
  # append tmp results to the main table
  df_intersections <- bind_rows(df_intersections, tmp)
}

lerm_lr <- df_intersections

lerm_lr %>% sample_n(10)
```

```{r}
# most repetitive words
lerm_lr %>% 
  unnest_tokens(input = words, output = word, token = "words") %>% 
  count(word, pos, sort = T)
```

### zeta

```{r}
# n adj
lerm_norm %>% 
  filter(pos == "A") %>% 
  count(corpus)

# prepare corpus with samples
corpus_prepared <- lerm_norm %>% 
  filter(pos == "A") %>% 
  group_by(corpus) %>% 
  sample_n(4000) %>% 
  mutate(sample_id = ceiling(1:4000),
         sample_id = floor(sample_id/2000)+1, 
         sample_id = ifelse(sample_id == 3, 1, sample_id)) %>% 
  ungroup() %>% 
  mutate(sample_id = paste0(corpus, "_", sample_id)) %>% 
  group_by(sample_id) %>% 
  summarise(text = paste0(lemma, collapse = "  ")) %>% 
  mutate(corpus = str_remove(sample_id, "_\\d+$"), 
         path = ifelse(corpus == "norm", "secondary_set/", "primary_set/"),
         path = paste0("zeta_tests/lerm_norm_00/", path, sample_id, ".txt"))

head(corpus_prepared)
```

```{r}
do.call(file.remove, list(
  list.files("zeta_tests/lerm_norm_00//primary_set", full.names = TRUE)))

do.call(file.remove, list(
  list.files("zeta_tests/lerm_norm_00//secondary_set", full.names = TRUE)))

for (i in 1:nrow(corpus_prepared)) {
  writeLines(corpus_prepared$text[i], corpus_prepared$path[i])
}
```

```{r}
oppose(
  gui = FALSE,
  path = "zeta_tests/lerm_norm_00/",
  corpus.lang = "Other",
  text.slice.length = 500,
  write.png.file = TRUE
)
```

```{r}
x <- readLines("zeta_tests/lerm_norm_00/words_preferred.txt")
x[8:17]

tibble(run = 1,
       words = paste(x[8:17], sep = " ", collapse = " "))
```

```{r}
df <- NULL
temp_df <- NULL
x <- NULL
```

```{r}

df <- NULL

stable_wd <- getwd()

for (pos_k in pos_key) {
  
  for (i in 1:100) {
  # I. select random poems for lermontov
  
    lerm_poems <- corpus %>% 
        filter(author_name == "Lermontov M.Ju.") %>% 
        # select small poems
        # filter(verses < 257) %>% 
        select(title) %>% 
        distinct() %>% 
        sample_n(270) %>% 
        pull()
      
      # select lermontov bigger sample
      lerm <- corpus %>% 
        filter(author_name == "Lermontov M.Ju.") %>% 
        # filter selected 300 poems
        filter(title %in% lerm_poems) %>% 
        
        mutate(pos = str_extract(analysis, "gr': '.*?,"),
               pos = str_remove_all(pos, "gr': '|=.*$|,")) %>% 
        select(id, author_name, title, lemma, pos) %>% 
        
        # NB sample 43000 words! to make it similar to original selection
        sample_n(43000) %>% 
        mutate(corpus = "lerm") %>% 
        rename(id_poem = id)
    
    # glimpse(lerm)
    lerm_norm <- rbind(lerm, norm)
    
  
  
    # II. prepare corpus with samples
    corpus_prepared <- lerm_norm %>% 
      filter(pos == pos_k) %>% 
      group_by(corpus) %>% 
      sample_n(1000) %>% 
      mutate(sample_id = ceiling(1:1000),
             sample_id = floor(sample_id/500)+1, 
             sample_id = ifelse(sample_id == 3, 1, sample_id)) %>% 
      ungroup() %>% 
      mutate(sample_id = paste0(corpus, "_", sample_id)) %>% 
      group_by(sample_id) %>% 
      summarise(text = paste0(lemma, collapse = "  ")) %>% 
      mutate(corpus = str_remove(sample_id, "_\\d+$"), 
             path = ifelse(corpus == "norm", "secondary_set/", "primary_set/"),
             path = paste0("zeta_tests/lerm_norm_00/", path, sample_id, ".txt"))
    
  
      # III. Remove old files & write new ones
      do.call(file.remove, list(
        list.files("zeta_tests/lerm_norm_00//primary_set", full.names = TRUE)))
      
      do.call(file.remove, list(
        list.files("zeta_tests/lerm_norm_00//secondary_set", full.names = TRUE)))
      
      for (j in 1:nrow(corpus_prepared)) {
        writeLines(corpus_prepared$text[j], corpus_prepared$path[j])
      }
  
    # IV. run zeta
    oppose(
      gui = FALSE,
      path = "zeta_tests/lerm_norm_00/",
      corpus.lang = "Other",
      text.slice.length = 250,
      write.png.file = TRUE
    ) # this function changes working dir, it;s likely that it's needed to change path below to run the loop properly
  
    # return normal wd
    setwd(stable_wd)
    
    x <- readLines("~/Documents/ucl/kjetsaa/scr/zeta_tests/lerm_norm_00/words_preferred.txt")
    x[8:17] # read top-10 words (first lines are comments to thelist)
  
    temp_df <- tibble(run = i,
                      pos = pos_k, 
                      words = paste(x[8:17], sep = " ", collapse = " "))
    
    df <- rbind(df, temp_df)
  } 
} 

df
```

```{r}
zeta_results <- df
```

```{r}
glimpse(zeta_results)
# 
# zeta_sep <- zeta_results %>% 
#   separate_rows(words, sep = " ")

df <- df %>% 
  separate_rows(words, sep = " ") %>% 
  rename(lemma = words)
```

```{r}
df_intersections <- tibble(pos = NULL,
                           run = NULL,
                           words = NULL,
                           n = NULL)
# temp var
x <- NULL

for (j in 1:length(pos_key)) {
  
  pos_k <- pos_key[j]
  
  # extract the list of the keywords based on pos
  x <- lerm_lists %>% 
    filter(pos == pos_k) %>% 
    pull(text) %>% 
    str_split("\\n") %>% 
    unlist()
  
  # select only top-10 words
  x <- x[1:10]

  # temp results for this pos
  tmp <- tibble()
  
  # loop to iterate over new results & calc intersection
  for (i in 1:100) {
  
    wl <- df %>% 
      filter(run == i, pos == pos_k) %>% 
      pull(lemma) 

    w <- intersect(x, wl) # can later look which words exactly
    n <- length(w)
    
    tmp <- bind_rows(tmp, tibble(
      pos = pos_k,
      run = i,
      words = paste(w, collapse = " "),
      n = n
    ))
  }
  
  # append tmp results to the main table
  df_intersections <- bind_rows(df_intersections, tmp)
}


lerm_zr <- df_intersections

glimpse(lerm_zr)
```

Count how much these lists are similar inside one keyness measurement

Count how much are they similar between each other

### Plot

```{r}

glimpse(lerm_gr)
glimpse(lerm_lr)
glimpse(lerm_zr)

pos_transl <- tibble(
  pos = c("A", "S", "V"),
  pos_tag = c("ADJ", "NOUN", "VERB")
)

lerm_gr %>% 
  mutate(group = "Guiraud") %>% 
  rbind(lerm_lr %>% mutate(group = "Weighted log odds ratio")) %>% 
  rbind(lerm_zr %>% mutate(group = "Zeta")) %>% 
  left_join(pos_transl, by = "pos") %>% 

  ggplot(aes(y = n, x = group, fill = group, colour = group)) + 
  geom_jitter(alpha = 0.5) + 
  geom_boxplot(alpha = 0.3) + 
  
  facet_wrap(~pos_tag, nrow = 3) + 
  labs(y = "Number of words found in both lists", 
       x = "Distinctiveness measure") + 
  scale_y_continuous(limits = c(0, 10), 
                     breaks = seq(1, 10, by = 1)) + 
  scale_fill_manual(values = c(met.brewer("Java")[1],
                               met.brewer("Java")[5],
                               met.brewer("Java")[4])) + 
  
  scale_colour_manual(values = c(met.brewer("Java")[1],
                               met.brewer("Java")[5],
                               met.brewer("Java")[4])) +
  theme(legend.position = "None",
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 18),
        strip.text = element_text(size = 18),
        #legend.text = element_text(size = 16), 
        plot.title = element_text(size = 20),
        )

ggsave("../plots/05_keywords_catch.png", plot = last_plot(),
       width = 8, height = 6, bg = "white", dpi = 300)
```

## II. larger corpus (10k)

```{r}
t <- read.csv("../data/kjetsaa_norm_corpus.csv")

t %>% 
  separate_rows(text_raw, sep = "\n")
```
