---
title: "02_keywords"
format: html
editor: visual
---

## Keywords analysis

## Load data & pckg

```{r}
library(tidyverse)
library(tidytext)
library(tidylo)
library(stylo)

library(MetBrewer)
theme_set(theme_minimal())
```

```{r}
# corpus with all words from RNC by 20 authors
corpus <- read.csv("../data/20authors_all_lemmatized.csv") %>% select(-X)

glimpse(corpus)
```

```{r}
norm <- read.csv("../data/kjetsaa_norm_lemmatized.csv")
glimpse(norm)
```

## I. small corpus replication

```{r}
lerm_poems <- corpus %>% 
  filter(author == "М. Ю. Лермонтов") %>% 
  select(header) %>% 
  distinct() %>% 
  sample_n(150) %>% 
  pull()

# select lermontov bigger sample
lerm <- corpus %>% 
  filter(author == "М. Ю. Лермонтов") %>% 
  # filter selected 300 poems
  filter(header %in% lerm_poems) %>% 
  
  mutate(pos = str_extract(analysis, "gr': '.*?,"),
         pos = str_remove_all(pos, "gr': '|=.*$|,")) %>% 
  select(id, author, header, lemma, pos) %>% 
  
  # NB sample 43000 words! to make it similar to original selection
  # sample_n(43000) %>% 
  mutate(corpus = "lerm")

glimpse(lerm)
```

Prepare 'norm' corpus for comparison

```{r}
norm <- norm %>% 
  mutate(pos = str_extract(analysis, "gr': '.*?,"),
         pos = str_remove_all(pos, "gr': '|=.*$|,")) %>% 
  select(id, author, header, lemma, pos) %>% 
  mutate(corpus = "norm")

glimpse(norm)
```

```{r}
colnames(lerm) == colnames(norm)

lerm_norm <- rbind(lerm, norm)
```

### base adj freq

MF adj in Lerm & in norm

```{r}
x <- lerm %>% 
  filter(pos == "A") %>% nrow() # number of adjectives

lerm %>% 
  filter(pos == "A") %>% 
  count(lemma, sort = T) %>% 
  mutate(perc = round(n/x * 100, 2 ))
```

```{r}
x <- norm %>% 
  filter(pos == "A") %>% nrow() # number of adjectives

norm %>% 
  filter(pos == "A") %>% 
  count(lemma, sort = T) %>% 
  mutate(perc = round(n/x * 100, 2 ))
```

```{r}
lerm %>% select(header) %>% distinct()
norm %>% select(header) %>% distinct()
```

### Giuraud coeff

```{r}
lerm_freq <- lerm %>% 
  filter(pos == "A") %>% 
  count(lemma, sort = T)

norm_freq <- norm %>% 
  filter(pos == "A") %>% 
  count(lemma, sort = T) %>% 
  rename(norm_n = n) 

lerm_counts <- lerm_freq %>% 
  left_join(norm_freq, by = "lemma")

lerm_counts %>% 
  mutate(t = (norm_n * nrow(lerm))/nrow(norm),
         diff = n - t,
         q = round(diff / sqrt(t), 2)) %>% 
  arrange(desc(q)) %>% 
  head(20)
```

#### sampled (10 runs)

```{r}
norm <- norm %>% 
  mutate(pos = str_extract(analysis, "gr': '.*?,"),
         pos = str_remove_all(pos, "gr': '|=.*$|,")) %>% 
  select(id, author, header, lemma, pos) %>% 
  mutate(corpus = "norm")

glimpse(norm)
```

(trying to) remove Lermontov's narrative poems

```{r}
corpus %>% 
  filter(author == "М. Ю. Лермонтов") %>% 
  arrange(desc(verses)) %>% 
  select(verses, header) %>% 
  distinct() %>% 
  head(30)

# number of short poems < 257 lines -- 453
corpus %>% 
  filter(author == "М. Ю. Лермонтов") %>% 
  arrange(desc(verses)) %>% 
  select(verses, header) %>% 
  distinct() %>% 
  filter(verses < 257) %>% nrow()
```

```{r}

df <- tibble()
x <- NULL

for (i in 1:100) {

  lerm_poems <- corpus %>% 
    filter(author == "М. Ю. Лермонтов") %>% 
    # select small poems
    filter(verses < 257) %>% 
    select(header) %>% 
    distinct() %>% 
    sample_n(150) %>% 
    pull()
  
  # select lermontov bigger sample
  lerm <- corpus %>% 
    filter(author == "М. Ю. Лермонтов") %>% 
    # filter selected 300 poems
    filter(header %in% lerm_poems) %>% 
    
    mutate(pos = str_extract(analysis, "gr': '.*?,"),
           pos = str_remove_all(pos, "gr': '|=.*$|,")) %>% 
    select(id, author, header, lemma, pos) %>% 
    
    # NB sample 43000 words! to make it similar to original selection
    # sample_n(43000) %>% 
    mutate(corpus = "lerm")
  
  # glimpse(lerm)
  
  lerm_freq <- lerm %>% 
    filter(pos == "A") %>% 
    count(lemma, sort = T)
  
  norm_freq <- norm %>% 
    filter(pos == "A") %>% 
    count(lemma, sort = T) %>% 
    rename(norm_n = n) 
  
  lerm_counts <- lerm_freq %>% 
    left_join(norm_freq, by = "lemma")
  
  x <- lerm_counts %>% 
    mutate(t = (norm_n * nrow(lerm))/nrow(norm),
           diff = n - t,
           q = round(diff / sqrt(t), 2)) %>% 
    arrange(desc(q)) %>% 
    head(10) %>% 
    mutate(run = i)

  df <- rbind(df, x)
}

df %>% sample_n(10)
```

Load Kjetsaa's list and calculate intersection

```{r}
adj_list_k <- readLines("../data/key_adj_lerm.txt")
adj_list_k

```

```{r}

df_intersections <- tibble(run = NULL,
                           words = NULL,
                           n = NULL)

for (i in 1:100) {
  wl <- df %>% 
    filter(run == i) %>% 
    pull(lemma) 

  w <- intersect(adj_list_k, wl) # can later look which words exactly
  n <- length(intersect(wl, adj_list_k))
  
  df_intersections[i, 1] <- i
  df_intersections[i, 2] <- paste(w, collapse = " ", sep = " ")
  df_intersections[i, 3] <- n
}

guiraud_results <- df_intersections

guiraud_results %>% 
  unnest_tokens(input = ...2, output = word, token = "words") %>% 
  count(word, sort = T)
```

### log odds

```{r}
lerm_norm %>% 
  filter(pos == "A") %>% 
  count(corpus, lemma, sort = T) %>% 
  bind_log_odds(corpus, lemma, n) %>% 
  arrange(-log_odds_weighted) %>% 
  group_by(corpus) %>% 
  slice_max(log_odds_weighted, n = 10) %>% 
  ungroup() %>% 
  mutate(lemma = reorder(lemma, log_odds_weighted)) %>% 
  ggplot(aes(x = log_odds_weighted, y = lemma, fill = corpus)) + 
  geom_col() + 
  facet_wrap(~corpus, scales = "free") + 
  labs(y = NULL)
```

```{r}
df <- tibble()
x <- NULL

for (i in 1:100) {

  lerm_poems <- corpus %>% 
    filter(author == "М. Ю. Лермонтов") %>% 
    # select small poems
    filter(verses < 257) %>% 
    select(header) %>% 
    distinct() %>% 
    sample_n(150) %>% 
    pull()
  
  # select lermontov bigger sample
  lerm <- corpus %>% 
    filter(author == "М. Ю. Лермонтов") %>% 
    # filter selected 300 poems
    filter(header %in% lerm_poems) %>% 
    
    mutate(pos = str_extract(analysis, "gr': '.*?,"),
           pos = str_remove_all(pos, "gr': '|=.*$|,")) %>% 
    select(id, author, header, lemma, pos) %>% 
    
    # NB sample 43000 words! to make it similar to original selection
    # sample_n(43000) %>% 
    mutate(corpus = "lerm")
  
  # glimpse(lerm)
  lerm_norm <- rbind(lerm, norm)
  
  x <- lerm_norm %>% 
    filter(pos == "A") %>% 
    count(corpus, lemma, sort = T) %>% 
    bind_log_odds(corpus, lemma, n) %>% 
    arrange(-log_odds_weighted) %>% 
    group_by(corpus) %>% 
    slice_max(log_odds_weighted, n = 10) %>% 
    ungroup() %>% 
    filter(corpus == "lerm") %>% 
    head(10) %>% 
    mutate(run = i)

  df <- rbind(df, x)
}

df %>% sample_n(10)
```

```{r}
df_intersections <- tibble(run = NULL,
                           words = NULL,
                           n = NULL)

for (i in 1:100) {
  wl <- df %>% 
    filter(run == i) %>% 
    pull(lemma) 

  w <- intersect(adj_list_k, wl) # can later look which words exactly
  n <- length(intersect(wl, adj_list_k))
  
  df_intersections[i, 1] <- i
  df_intersections[i, 2] <- paste(w, collapse = " ", sep = " ")
  df_intersections[i, 3] <- n
}

logodds_results <- df_intersections

# most repetitive word:
logodds_results %>% 
  unnest_tokens(input = ...2, output = word, token = "words") %>% 
  count(word, sort = T)
```

### zeta

```{r}
# n adj
lerm_norm %>% 
  filter(pos == "A") %>% 
  count(corpus)

# prepare corpus with samples
corpus_prepared <- lerm_norm %>% 
  filter(pos == "A") %>% 
  group_by(corpus) %>% 
  sample_n(4000) %>% 
  mutate(sample_id = ceiling(1:4000),
         sample_id = floor(sample_id/2000)+1, 
         sample_id = ifelse(sample_id == 3, 1, sample_id)) %>% 
  ungroup() %>% 
  mutate(sample_id = paste0(corpus, "_", sample_id)) %>% 
  group_by(sample_id) %>% 
  summarise(text = paste0(lemma, collapse = "  ")) %>% 
  mutate(corpus = str_remove(sample_id, "_\\d+$"), 
         path = ifelse(corpus == "norm", "secondary_set/", "primary_set/"),
         path = paste0("zeta_tests/lerm_norm_00/", path, sample_id, ".txt"))

head(corpus_prepared)
```

```{r}
do.call(file.remove, list(
  list.files("zeta_tests/lerm_norm_00//primary_set", full.names = TRUE)))

do.call(file.remove, list(
  list.files("zeta_tests/lerm_norm_00//secondary_set", full.names = TRUE)))

for (i in 1:nrow(corpus_prepared)) {
  writeLines(corpus_prepared$text[i], corpus_prepared$path[i])
}
```

```{r}
oppose(
  gui = FALSE,
  path = "zeta_tests/lerm_norm_00/",
  corpus.lang = "Other",
  text.slice.length = 500,
  write.png.file = TRUE
)
```

```{r}
x <- readLines("zeta_tests/lerm_norm_00/words_preferred.txt")
x[8:17]

tibble(run = 1,
       words = paste(x[8:17], sep = " ", collapse = " "))
```

```{r}
df <- NULL
temp_df <- NULL
x <- NULL
```

```{r}



# I. select random poems for lermontov

  lerm_poems <- corpus %>% 
    filter(author == "М. Ю. Лермонтов") %>% 
    # select small poems
    filter(verses < 257) %>% 
    select(header) %>% 
    distinct() %>% 
    sample_n(150) %>% 
    pull()
  
  # select lermontov bigger sample
  lerm <- corpus %>% 
    filter(author == "М. Ю. Лермонтов") %>% 
    # filter selected 300 poems
    filter(header %in% lerm_poems) %>% 
    
    mutate(pos = str_extract(analysis, "gr': '.*?,"),
           pos = str_remove_all(pos, "gr': '|=.*$|,")) %>% 
    select(id, author, header, lemma, pos) %>% 
    
    # NB sample 43000 words! to make it similar to original selection
    # sample_n(43000) %>% 
    mutate(corpus = "lerm")
  
  # glimpse(lerm)
  lerm_norm <- rbind(lerm, norm)
  


  # II. prepare corpus with samples
  corpus_prepared <- lerm_norm %>% 
    filter(pos == "A") %>% 
    group_by(corpus) %>% 
    sample_n(1000) %>% 
    mutate(sample_id = ceiling(1:1000),
           sample_id = floor(sample_id/500)+1, 
           sample_id = ifelse(sample_id == 3, 1, sample_id)) %>% 
    ungroup() %>% 
    mutate(sample_id = paste0(corpus, "_", sample_id)) %>% 
    group_by(sample_id) %>% 
    summarise(text = paste0(lemma, collapse = "  ")) %>% 
    mutate(corpus = str_remove(sample_id, "_\\d+$"), 
           path = ifelse(corpus == "norm", "secondary_set/", "primary_set/"),
           path = paste0("zeta_tests/lerm_norm_00/", path, sample_id, ".txt"))
  

    # III. Remove old files & write new ones
    do.call(file.remove, list(
      list.files("zeta_tests/lerm_norm_00//primary_set", full.names = TRUE)))
    
    do.call(file.remove, list(
      list.files("zeta_tests/lerm_norm_00//secondary_set", full.names = TRUE)))
    
    for (j in 1:nrow(corpus_prepared)) {
      writeLines(corpus_prepared$text[j], corpus_prepared$path[j])
    }

  # IV. run zeta
  oppose(
    gui = FALSE,
    path = "zeta_tests/lerm_norm_00/",
    corpus.lang = "Other",
    text.slice.length = 250,
    write.png.file = TRUE
  ) # this function changes working dir, it;s likely that it's needed to change path below to run the loop properly

  x <- readLines("~/Documents/ucl/kjetsaa/scr/zeta_tests/lerm_norm_00/words_preferred.txt")
  x[8:17]

tail(df)  

temp_df <- tibble(run = 20,
         words = paste(x[8:17], sep = " ", collapse = " "), 
         group = "Zeta")
  
df <- rbind(df, temp_df)

df
```

```{r}
zeta_reults <- df
zetas <- df
```

```{r}
glimpse(zetas)

zeta_sep <- zetas %>% 
  separate_rows(words, sep = " ")
```

```{r}
df_intersections <- tibble(run = NULL,
                           words = NULL,
                           n = NULL)

for (i in 1:20) {
  wl <- zeta_sep %>% 
    filter(run == i) %>% 
    pull(words) 

  w <- intersect(adj_list_k, wl) # can later look which words exactly
  n <- length(intersect(wl, adj_list_k))
  
  df_intersections[i, 1] <- i
  df_intersections[i, 2] <- paste(w, collapse = " ", sep = " ")
  df_intersections[i, 3] <- n
}

zeta_results <- df_intersections

zeta_results
```

Count how much these lists are similar inside one keyness measurement

Count how much are they similar between each other

### Plot

```{r}

glimpse(guiraud_results)
glimpse(logodds_results)
glimpse(zeta_results)


guiraud_results %>% 
  mutate(group = "Guiraud") %>% 
  rbind(logodds_results %>% mutate(group = "Weighted log odds ratio")) %>% 
  rbind(zeta_results %>% mutate(group = "Zeta")) %>% 
  rename(run = ...1, 
         words = ...2, 
         n = ...3) %>% 
  ggplot(aes(y = n, x = group, fill = group)) + 
  geom_boxplot() + 
  labs(y = "Number of words found in both lists (10 adjectives)", 
       x = "Distinctiveness measure") + 
  scale_y_continuous(limits = c(0, 10), 
                     breaks = seq(1, 10, by = 1)) + 
  scale_fill_manual(values = c(met.brewer("Java")[1],
                               met.brewer("Java")[5],
                               met.brewer("Java")[4])) + 
  theme(legend.position = "None",
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 18),
        #legend.text = element_text(size = 16), 
        plot.title = element_text(size = 20))

ggsave("../plots/05_keywords_catch.png", plot = last_plot(),
       width = 8, height = 6, bg = "white", dpi = 300)
```

## II. larger corpus (10k)

```{r}
t <- read.csv("../data/kjetsaa_norm_corpus.csv")

t %>% 
  separate_rows(text_raw, sep = "\n")
```
